---
title: "Friends Don't Let Friends Use Pie Charts"
linktitle: "Week 1: Friends Don't Let Friends Use Pie Charts"
output:
  blogdown::html_page:
    toc: true
menu:
  due:
    parent: Due?
    weight: 2
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

```{r eval = TRUE, echo = FALSE}
unchecked <- as.character(fontawesome::fa("circle", fill = "#e4e4e4", height = "15px"))

checked <- as.character(fontawesome::fa("check-circle", fill = "#428bca", height = "15px"))

wk_post <- tibble(
  

"Data Camp" = c(unchecked,
            unchecked,
            unchecked,
            unchecked,
            unchecked,
            checked),

"eCampus" = c(unchecked,
        unchecked,
        unchecked,
        unchecked,
        unchecked,
        unchecked),

"R" = c(checked,
        unchecked,
        unchecked,
        unchecked,
        unchecked,
        checked),

"Slack" = c(unchecked, 
              unchecked, 
              unchecked,
              checked,
              checked,
              unchecked),

Description = c("Install Course Software",
                "Read a few things",
                "Look over the website",
                "Get into the course Slack account",
                "Find a bad graphic",
                "Complete Introduction to R"),

Location = c("[Link](/resource/install/)",
             "[Link](/readings/01-readings/#read-things)",
             "[Link](/readings/01-readings/#review-the-rest)",
             "[Link](/assignment/01-assignment/#class-slack-account-access)",
             "[Link](/assignment/01-assignment/#find-a-bad-graphic)",
             "[Link](https://www.datacamp.com/){target='_blank'}"))
```

### What's Due?
<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(wk_post, 
      escape = FALSE,
      align = 'cccclc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "10em") %>%
  column_spec(5, width = "15em") %>% 
  row_spec(0, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(2, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(3, extra_css = 'vertical-align: middle !important;') 
```
</center>

*Note: These tasks are provided in a recommended order.*
