---
title: "Exactly What is Mixed Methods Research?"
linktitle: "Week 1: Exactly What is Mixed Methods Research?"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  trainings:
    parent: Modules
    weight: 1
type: docs
weight: 1
---

`r blogdown::shortcode("aes-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

## Notes

### for previous participants
If you have participated in Data Camp before and would like to receive credit for assigned modules you have previously completed, make sure to login with the associated username. Please note that you must do this to qualify. 

### for new participants
Please take your time with these modules. I suggest Weekting 3-4 hours for this initial Week and go work in a way that's conducive to your learning. The first module gives you an understand of the R environment while the second deals assigned next Week deals with data wrangling and reshaping, namely making sure data is in what we call a "tidy" format. All analyses will be required to be performed in R. Please reach out if you need help!

## Installing R and RStudio (soon to be called Posit)
Go to the [Installing R, RStudio, and tidyverse](/resources/install/) page under Resources to get both R and RStudio installed on your system.

## Data Camp

Please begin the following module

```{r eval = TRUE, echo = FALSE, message=FALSE}
dc_schedule <-  
  read_csv(here::here("content", "dc.csv"),
           show_col_types = FALSE) %>%
  as_tibble() %>%
  mutate(Required = case_when(
    Required == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
    Required == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px"))
      )
    ) %>%
  mutate(Task = case_when(
    Task == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
    Task == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px"))
      )
    ) %>%
  filter(Week == 1) %>% #CHANGE HERE
  select(-Week) %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), str_squish)) %>%
  rename(`Due by` = Due) %>%
#  filter_all(any_vars(!is.na(.))) %>% 
  mutate(
    across(everything(), ~replace_na(.x, ""))
    ) %>%
  select_if(~!all(is.na(.)))
  
```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(dc_schedule, 
      "html", 
      escape = FALSE,
      align = 'ccccll') %>%
  kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "8em") %>%
  column_spec(6, width = "8em") %>%
  row_spec(0:nrow(dc_schedule), extra_css = 'vertical-align: middle !important;', color = "#f7f7f7", background = "transparent")
```
</center>
