---
title: "Detailing Studies"
linktitle: "Week 8: Detailing Studies"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  trainings:
    parent: Modules
    weight: 8
type: docs
weight: 1
---

`r blogdown::shortcode("r-walkthrough-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

## Data Camp

Please begin the following module

```{r eval = TRUE, echo = FALSE, message=FALSE}
dc_schedule <-  
  read_csv(here::here("content", "dc.csv"),
           show_col_types = FALSE) %>%
  as_tibble() %>%
  mutate(Required = case_when(
    Required == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
    Required == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px"))
              )) %>%
  mutate(Task = case_when(
    Task == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
    Task == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px"))
      )
    ) %>%
  filter(Set == 6) %>% #CHANGE HERE
  select(-Set) %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), str_squish)) %>%
  rename(`Due by` = Due) %>%
#  filter_all(any_vars(!is.na(.))) %>% 
  mutate(
    across(everything(), ~replace_na(.x, ""))
    ) %>%
  select_if(~!all(is.na(.)))
  
```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(dc_schedule, 
      "html", 
      escape = FALSE,
      align = 'ccccll') %>%
  kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "8em") %>%
  column_spec(6, width = "8em") %>%
  row_spec(0:nrow(dc_schedule), extra_css = 'vertical-align: middle !important;', color = "#f7f7f7", background = "transparent")
```
</center>

## R Task

Please follow the directions listed below

1. Download the task files

<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "rtasks", "Joins.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Joins Task",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
</center>
<br>

2. [Unzip](/resources/unzipping) them on your computer

3. Open the file `Joins Install.R` and run the syntax to install the packages you will need for this task

4. Open the file `Joins walkthrough.Rmd` in RStudio

5. After finishing the walkthrough, open the mostly empty Rmarkdown file `Joins Report.Rmd`, read through the body, and please make changes as directed to receive credit

6. Save the resulting PDF file by adding your first initial and last name to the beginning of the filename. For example, my submission would be `aroy Joins walkthrough.pdf`

8. Submit the script to [eCampus](https://ecampus.wvu.edu) in the Submission Portal
