---
title: "Preparing for Distribution"
linktitle: "Week 8: Preparing for Distribution"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  trainings:
    parent: Modules
    weight: 8
type: docs
weight: 1
---

`r blogdown::shortcode("r-walkthrough-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

## Refresher 

If you need a review of Linear Regression, take a look at Dr. Josh Starmer's quirky but excellent video below

<p align="center">
  <iframe width="560" height="315" src="https://www.youtube.com/embed/nk2CQITm_eo" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</p>

## Data Camp

Please go through and complete the following module

```{r eval = TRUE, echo = FALSE, message=FALSE}
dc_schedule <-  
  read_csv(here::here("content", "dc.csv"),
           show_col_types = FALSE) %>%
  as_tibble() %>%
  mutate(across(everything(), ~ case_when(
    . == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
    . == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px")),
    TRUE ~ as.character(.)
              ))) %>%
  filter(Week == "8") %>% #CHANGE HERE
  select(-Week) %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), str_squish)) %>%
  rename(`Due by` = Due) %>%
#  filter_all(any_vars(!is.na(.))) %>% 
  mutate(
    across(everything(), ~replace_na(.x, ""))
    ) %>%
  select_if(~!all(is.na(.)))
  
```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(dc_schedule, 
      "html", 
      escape = FALSE,
      align = 'ccccll') %>%
  kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "12em") %>%
  column_spec(6, width = "12em") %>%
  row_spec(0:nrow(dc_schedule), extra_css = 'vertical-align: middle !important;', color = "#f7f7f7", background = "transparent")
```
</center>


## R Task

Please follow the directions listed below

1. Download the task files

<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "rtasks", "Simple Regression.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Simple Regression Task",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
</center>
<br>

2. [Unzip](/resources/unzipping) them on your computer and place all of the files in a folder of your choice as is

3. Open the file `Simple Regression Install.R` and run the syntax to install the **pacman** package. This can be used not just to load libraries, but if you are missing any then those will be downloaded automatically by R

4. Open the file `Simple Regression walkthrough.Rmd` in RStudio

5. After finishing the walkthrough, open the mostly empty Rmarkdown file `Simple Regression Report.Rmd`, read through the directions, and include your syntax to receive credit. You are provided an optional `Simple Regression test script.R` to test your R code as needed.

6. Save the resulting PDF file by adding your first initial and last name to the beginning of the filename. For example, my submission would be `aroy Simple Regression walkthrough.pdf`

8. Submit the script to [eCampus](https://ecampus.wvu.edu) in the Submission Portal
