---
title: "R Project"
author: "NAME" # Erase this comment and please change NAME to your name
output: pdf_document
---

```{r libraries, warning=FALSE, message=FALSE}
library("tidyverse")
library("psych")
library("corrr")
library("surveytools2")
library("naniar")
library("mice")
```


```{r load_your_data_and_codebook}
# erase this comment and paste your syntax here 
```

```{r load_your_data_results}
# erase this comment and put the variable name used above for the data set here 
```

```{r load_your_codebook_results}
# erase this comment and put the variable name used above for the codebook here 
```


# Possible Reverse Coding

```{r items_that_need_reverse_coded}
# If any items needs reverse coded, (1) erase this comment and first paste the syntax used to determine which item(s)
```

DELETE THIS AND DESCRIBE WHICH ITEMS NEED TO BE REVERSE CODED AND WHY.

```{r reverse_coding}
# (2) erase this comment and then paste the syntax used to perform the reverse coding
```

```{r reverse_coding_results}
# erase this comment and put the variable name used above here 
```


# Test for MCAR and Possible Imputation

```{r test_for_mcar}
# erase this comment and paste your syntax here 
```

DELETE THIS AND DESCRIBE IF THE IF YOU WILL BE IMPUTING THE DATA OR NOT. PLEASE PROVIDE A JUSTIFICATION.

```{r imputation, results='hide'}
# if you concluded that imputation is needed, erase this comment and paste your syntax here
```

```{r imputation_results}
# erase this comment and display the first six rows of the imputed data set using the variable name used above
```

```{r missing_values_comparison}
# erase this comment and include syntax comparing the number of missing values in the original data set versus the imputed one
```

DELETE THIS AND DESCRIBE THE NUMBER OF MISSING VALUES IN THE ORGINAL DATA SET IN COMPARISON TO THE IMPUTED ONE.


# Test of Validity

```{r scree}
# erase this comment and then paste the syntax used to plot a scree plot
```

DELETE THIS AND DESCRIBE THE NUMBER OF LIKELY FACTORS NEEDED.

```{r efa}
# erase this comment and then paste the syntax used to conduct an EFA
```

```{r efa_loadings_results}
# erase this comment and then paste the syntax used to see the loadings
```

```{r efa_diagram}
# erase this comment and then paste the syntax used to plot the FA diagram
```

DELETE THIS AND DESCRIBE (1) WHETHER THE ORIGINAL GROUP DESCRIBED IN THE CODEBOOK ARE LIKELY CORRECT AND (2) IF NOT, CREATE INTERPRETATIONS OF THE NEW GROUPS. 


# Reliability 

```{r relibility}
# erase this comment and then paste the syntax used to conduct a test for reliability
```

```{r internal_consistency}
# erase this comment and then paste the syntax used to present a table that arranges survey items by descending internal consistency measures
```

```{r internal_consistency_results}
# erase this comment and put the variable name used above here 
```

DELETE THIS AND INTERPRET THE RELIABILITY OF THE INSTRUMENT

# Conclusion

DELETE THIS AND DESCRIBE IF THE INSTRUMENT IS LIKELY BOTH VALID AND RELIABLE. PLEASE PROVIDE JUSTIFICATIONS FROM YOUR WORK ABOVE. IF THE INSTRUMENT IS NOT EITHER/OR, PLEASE DESCRIBE HOW YOU WOULD AMEND THE INSTRUMENT BEFORE IT IS ADMINISTERED AGAIN.
