---
title: "What? How Can you Frame a Data?"
subtitle: "EDP 613"
author: "Week 2"
output: 
 xaringan::moon_reader:
   css: xaringan-themer.css
---

```{r echo = FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#bb86fc",
  header_font_google = xaringanthemer::google_font("Jost", "600"),
  text_font_google   = xaringanthemer::google_font("Jost", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
```

# Looking at Data Like You're Used to
>- We nearly always look at data by rows and columns! 
>- In Excel, that format is called a cell structure.
>- In R, that format is called a data frame.

---

## First Things First!
Let's do the following:

>- Create a folder with subfolders by class week (e.g. Week 2, Week 3, etc.) somewhere on your hard drive where you can stick all of the R stuff. 
>- Go back to RStudio.
>- Use **File > New File > R Script** to create a new script.
>- Save it with a name ending in `.r` or `.R` in the new folder or subfolder you created.
>- Type in `getwd()` in the Console. If that doesn't look right, do this: **Session > Set Working Directory > To Source File Location**

---

## Data Frames: A Very Basic Rundown

>- Shows data in rows and columns.
>- Is really good for manipulating data.
>- Closest thing to Excel.

---

## Get the Gapminder data and load it up

We will work with some of the data from the [Gapminder project](https://www.gapminder.org/).

```{r echo = TRUE, eval = FALSE}
install.packages("gapminder")
```

```{r echo = TRUE}
library(gapminder)
```

---

## Look at the variables inside a data frame

>- To specify a single variable from a data frame, use the dollar sign `$`.

```{r  echo = TRUE}
head(gapminder$lifeExp)
```

```{r  echo = TRUE}
summary(gapminder$lifeExp)
```

---

## Plotting

>- We can visualize the data.

```{r echo = TRUE}
hist(gapminder$lifeExp)
```

---

## Getting underlying information about our data

```{r echo = TRUE}
class(gapminder$continent)
```


```{r echo = TRUE}
summary(gapminder$continent)
```

---

## Levels

```{r echo = TRUE}
levels(gapminder$continent)
```

>- The __levels__ of the factor `continent` are "Africa", "Americas", etc.

```{r echo = TRUE}
nlevels(gapminder$continent)
```

>-  __nlevels__ tells you how many there are.

---

## We can see the data about levels

```{r echo = TRUE}
table(gapminder$continent)
```

---

## And we can even plot them!

```{r echo = TRUE}
barplot(table(gapminder$continent))
```

---

## That's it for today!
