---
title: General Criteria for Visualizations
date: "2020-07-15"
menu:
  resource:
    parent: Resources
type: docs
weight: 5
output:
  blogdown::html_page:
      toc: TRUE
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(knitr)
library(kableExtra)
```

While there is no specific rubric, here is a basic outline of what to be looking out for in each task. Criteria will generally be graded on a competency-based scale roughly translating to 

+ **A: Exceeds expectations**, 
+ **B: Meets expectations**, 
+ **C: Needs improvement**, 
+ **D: Unsatisfactory**, and 
+ **F: Overall Failing**. 

Of course this is a continuous scale so a combination of proficiencies may be assigned to work that falls between any two consecutive levels.

<center>
```{r, echo=FALSE, warning=FALSE, message=FALSE}
read_csv("rubricish.csv") %>% 
      as_tibble() %>%
      
  kbl("html", 
      escape = FALSE,
      align = 'clllll') %>%
  column_spec(1, 
              bold = TRUE)
```
</center>


