---
title: "About the Trainings"
menu:
  trainings:
    parent: Overview
    weight: 1
type: docs
weight: 1
shiny: true
---

`r blogdown::shortcode("aes-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

Most class sessions have both interactive **Modules** courtesy of [Data Camp](https://www.datacamp.com/)^[Please note that if you have (1) used Data Camp before and (2) are logged in with the same username, then any module that was successfully completed will not have to be done again.] and **Walkthroughs** created by me that you will need to work through ***after*** doing the readings and reviewing the corresponding content (if applicable). The lessons are a central part of the class and are focused on using the [tidyverse](https://www.tidyverse.org/) family of packages, though the approaches are certainly not the only ways to wrangle, clean, analyze, and visualize data in R. 

### Advice
Carve out some time everyday to go through these. If you try to complete everything in one sitting, it will probably be overwhelming! However if you have familiarity with some modules, please feel free to work ahead.

### Grading
The ultimate point of Data Camp is to get you familiarized with an environment that you likely have never seen or been exposed to. While you should absolutely go through each module, there is certainly no expectation that you will get everything right. In fact, the points that you incur don't mean anything as far as how you are assessed so please use hints as needed! As with any things data science, you'll learn by doing. If you have a polar personality type as it pertains to work (i.e. primarily a perfectionist or mostly careless), then the modules will likely prove to be a challenge. It is highly unlikely that you will be able to comprehend everything by going beyond your limit or that it will just come to you so please work hard but also take breaks, swear^[and curse my name if you have to], and ask peers or me for help. Your score is predicated on putting in a solid effort, rather than getting it perfect because everything is probabilistic and nothing is for certain. 

### Data Camp Schedule

A *tentative* schedule is given below. The **Course** and **Chapter** names represent Data Camp titles^[Subject to change with notice.]:

#### Required
The following modules are required and will count toward your final grade

```{r eval = TRUE, echo = FALSE, message=FALSE}
unchecked <- as.character(fontawesome::fa("square", fill = "steelblue"))

checked <- as.character(fontawesome::fa("square-check", fill = "steelblue"))

dc_schedule <- 
  read_csv(here::here("content", "dc.csv"),
           show_col_types = FALSE) %>% 
  as_tibble()  %>%
  mutate(Required = case_when(
    Required == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
    Required == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px"))
      )
    ) %>%
  # select(-Group, -Chapters_long, -`Due by_short`) %>%
  rename(`Due by` = Due) %>%
  mutate(
    across(everything(), ~replace_na(.x, ""))
    )
```


```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(dc_schedule %>%
        filter(str_detect(Week, "Extra Credit|Recommended", negate = T)) %>%
  select(-Week), 
      "html", 
      escape = FALSE,
      align = 'llcll') %>%
  kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "20em") %>%
  column_spec(5, width = "20em") %>%
  row_spec(0:nrow(dc_schedule %>%
        filter(str_detect(Week, "Extra Credit|Recommended", negate = T))), 
        extra_css = 'vertical-align: middle !important;', 
        color = "#f7f7f7", 
        background = "transparent")
```

#### Extra Credit
The following modules are optional and may count as extra credit if successfully completed 

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(dc_schedule %>%
        filter(str_detect(Week, "Recommended")) %>%
  select(-Week, -Link), 
      "html", 
      escape = FALSE,
      align = 'ccll') %>%
  kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "20em") %>%
  column_spec(4, width = "20em") %>%
  row_spec(0:nrow(dc_schedule %>%
        filter(str_detect(Week, "Recommended"))), 
        extra_css = 'vertical-align: middle !important;', 
        color = "#f7f7f7", 
        background = "transparent")
```
</center>

#### Recommended
The following modules are optional but highly recommended
<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(dc_schedule %>%
        filter(str_detect(Week, "Extra Credit")) %>%
  select(-Week, -Link, -'Due by'), 
      "html", 
      escape = FALSE,
      align = 'cll') %>%
  kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "20em") %>%
  row_spec(0:nrow(dc_schedule %>%
        filter(str_detect(Week, "Extra Credit"))), 
        extra_css = 'vertical-align: middle !important;', 
        color = "#f7f7f7", 
        background = "transparent")
```
</center>


### Need Help?

`r blogdown::shortcode("meetings")`
