---
title: "How Data Doesn't Care About Your Beliefs or Feelings and Other Obviuous Observations I've Had to Tell People for Some Reason"
linktitle: "2: Neverending Designs, Measures, and Methods"
output:
  blogdown::html_page:
    toc: true
menu:
  example:
    parent: Examples
    weight: 2
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(widgetframe_self_contained = TRUE) 
knitr::opts_knit$set(root.dir = getwd())

library(tidyverse)
library(fivethirtyeight)
```

# Introduction

First things first, once a package has been loaded, you can use a `?` in front of any command to get more information about it. Sometimes the descriptions and/or examples aren't very helpful, but most of the time you should be able to find the information you are looking for. 

## Expectations

If you skim through this, you may notice that all of the outputs are already done for you. I strongly encourage you to take some time to go through these walkthroughs and to ask questions as needed! Much like any other language, R requires fluency but that cannot occur without a good foundation.

## Prerequisites {-}

In this session, we will use the `tidyverse` and `fivethirtyeight` packages. If you have loaded the former, then please skip ahead to the next paragraph. If not, please select **Tools > Install Packages** and then type in `tidyverse` and ensure that **Install dependencies** is selected or simply run the following in your console.

```{r eval=FALSE}
install.packages("tidyverse", dependencies = TRUE)
```

followed by 

```{r eval=FALSE}
library("tidyverse")
```

to load the family. Now try doing the same for `fivethirtyeight` by running

```{r eval=FALSE}
install.packages("fivethirtyeight", dependencies = TRUE)
```

followed by 

```{r eval=FALSE}
library("fivethirtyeight")
```

Please note that once a package is on your computer, you never have to install it again unless it is somehow deleted. This means from now on you will only have to use the second command `library("WHATEVER PACKAGE YOU ALREADY HAVE DOWNLOADED")` to use that package.

Before moving on, here is a good place to reiterate how you can use `?` to find more information. When you look at the package list for `fiverthirtyeight`, not all of the names do a great job of describing what that data set consists of. To see this, type in `fiverthirtyeight::` and scroll through the pop up list of available data sets and commands. Let's say the data set `tarantino` caught your eye but you weren't really sure what it consisted of. Hovering over the set in that pop up list tells you that it *contains data behind the story A Complete Catalog Of Every Time Someone Cursed Or Bled Out In A Quentin Tarantino Movie*. 

OK well that's a good start but to be able to do anything with that data, we really need to know what its variables are. To do this, run the command below

```{r}
?tarantino
```

You should have noticed the **Help** tab on the lower right hand window is prominent and there is a significant amount of information explaining the data set including the variable names and corresponding descriptions.

## Data Files

Data sets used in R are typically accessible in one of two ways.

1. They can be distributed within R packages. These are often smaller data sets used in examples, interactive guides, or tutorials within packages. These are loaded with the `data()` function. For example you can load UN data on demographic statistics from the **fivethirtyeight** library, which has plenty of data sets used by the poll analysis site [FiveThirtyEight](https://fivethirtyeight.com/){target="_blank"}. To see the entire list, you can run the command `data()`. In this case, the `drinks` data set looks like something I may want to look at. To view the data set, run

```{r}
data("drinks", package = "fivethirtyeight")
```

followed by

```{r}
drinks
```

2. They can be loaded from external files including both stored R file formats `.RData` and `.rda`, and other more familiar formats such as `.csv` and `.sav`. In this session, we'll look at reading and writing a [csv](https://en.wikipedia.org/wiki/Comma-separated_values){target="_blank"} file using R by enabling the commands `read_csv` and `write_csv` from the `readr` library (which is a part of `tidyverse` so you don't have to load it separately). 

The `drinks` data set can also be found [here](https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv){target="_blank"}. As long as data is somewhere and accessible, chances are R can get it! For example, we can use the `read_csv` command to get the data we need like so 

```{r}
drinks <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")
```

followed by

```{r}
drinks
```

As you can see from the outputs are identical. While you were typing you may have noticed that that there is a `read.csv()` and `read_csv()`. The former is what we call a base command, or one that is pre-built into R. However, you will want to stick to the latter which is from the `readr` package for many reasons we will get into later on, but for now just know it is a bit faster and returns a `tibble` instead of a data frame which is far easier to work with! You can check what type of variable you have  by using `class()` on it. For example, the following

```{R}
class(drinks)
```

tells us that we not only have a data frame, but a tibble as well as well as some other formats we'll ignore for the time being. If you want more information, please see [R for Data Science](http://r4ds.had.co.nz/) [Ch 10: Tibbles](http://r4ds.had.co.nz/tibbles.html#introduction-4).

Note that we loaded the file directly from a web address URL, but say you had it as a local file on your computer in the same directory as your R script. The command 

```{r eval=FALSE}
drinks <- read_csv("drinks.csv")

drinks
```

would work just as well. 

### Chopping a Data Set Up
You may already know that the single bracket, `[`, is useful to select rows and columns in simple cases.

```{r}
drinks[c(1, 2, 3, 4, 5), ]
```

There are `tidyverse` options to handle this via the package `dplyr` to select rows by number, to select rows by certain criteria, or to select columns.

For example, to select rows 1--5, we can use the `slice()` command.

```{r}
slice(drinks, 1:5)
```

Base R allows you to choose the column `beer_servings` from the `drinks` data frame in a number of ways. For example, each of the following

```{r eval=FALSE}
drinks[, "beer_servings"]
drinks$beer_servings
drinks[["beer_servings"]]
```

yields 

```{r echo=FALSE, eval=TRUE}
drinks$beer_servings
```

Unlike `[`, the `[[` and `$` operators can only select a single column and return a vector.[^extract1]
The `dplyr` function `select()` **always** returns a tibble, and never a vector, even if only one column is selected.

For example, note that selecting rows 1--5 of the `beer_servings` column using base R gives us a vector.

```{r}
drinks[1:5, "beer_servings"]
```

Whereas in the `dplyr` world, the same series of functions can be performed using a pipe operator: `%>%` which retains the table like format.

```{r}
drinks %>%
  slice(1:5) %>%
  select(beer_servings)
```

This example may seem verbose, but later we can produce more complicated transformations of the data by chaining together simple functions. For example, it is far easier to use them to select multiple columns like so

```{r}
drinks %>%
  slice(1:5) %>%
  select(country, beer_servings)
```

or to get rid of a column

```{r}
drinks %>%
  slice(1:5) %>%
  select(-spirit_servings)
```

We'll talk more about pipes next week! 

### Saving Objects

There are two types of saves you should consider at this point

- The workspace save
- An output save

The workspace save is everything you see in your RStudio window (e.g. the syntax, script, outputs, etc). When you close out of RStudio, you may be asked to save your workspace which essentially means the next time you load a saved script up, you'll pick up exactly where you left off. 

While convenient, it is not recommended that do this. Like rebooting a computer, you really want to have a fresh start every time RStudio starts up. While certainly not mandated, you never know what piece of rogue commands could have affected your progress when you last saved the file. Opting not to save an image of your workspace removes all of the previous commands while keeping your script intact. 

An output save occurs when you are trying to save a data set or result in a particular format. Firstly, you have to ensure that you have both downloaded and loaded a necessary package. For example, base R does not have an ability to read in and flatten SPSS files. However, installing and enabling the package `foreign` makes both reading in and writing to SPSS a cinch. 

Let's say we want to export our `drinks` output to a csv file. Well luckily we have the package `readr` already loaded and it has the command `write_csv()` that does exactly what we want. The command requires that you note the variable name, `drinks`, and what you want to call it which in this case I am calling `new_drinks.csv`. If you are wondering, you absolutely have to out the format type at the end. 

```{r eval=FALSE}
write_csv(drinks, "new_drinks.csv")
```

Well that's great but say we wanted to save it as a SPSS file. Running

```{r}
?write_csv
```

doesn't yield any information about saving any data set or output as a SPSS file. If we run a simple Google search (e.g. with the terms *save SPSS R tidy*) and click on the first link, it seems like a package called `haven` both saves a data frame as a SPSS file and is tidy as well which the package `foreign` I mentioned earlier does not. While the latter condition isn't required, having packages that do keep your data tidy will make your life **so much easier**! Now we can just do the following 

```{r eval=FALSE}
write_sav(drinks, "new_drinks.sav") 
```

Now you are free to go use SPSS for some reason.

### Style Guide

Following a consistent coding style is important for your code to be readable by you and others. The preferred style is the [tidyverse style guide](http://style.tidyverse.org/){target="_blank"}, which differs slightly from [Google's R style guide](http://style.tidyverse.org/){target="_blank"}.

-   The [lintr](https://github.com/jimhester/lintr){target="_blank"} package will check files for style errors.

-   The [styler](https://github.com/r-lib/styler){target="_blank"} package provides functions for automatically formatting R code according to style guides.

You will be expected to turn in a script with any submission where R is needed. Much like any writing, if your script is easy to read, then it is most likely easy to grade. A messy script without comments, spacing, and style may lead to misunderstandings. Long story short: make it look good and easy to interpret and your score will reflect that!

If you want a warning about styling your script, open  RStudio and go to the **Tools > Global Options > Code > Diagnostics** pane. Then check the box to activate style warnings. On this pane, there are other options that can be set in order to increase or decrease the amount of warnings while writing in RStudio.

[^setwd]: For more on using projects read [Project-oriented workflow](https://www.tidyverse.org/articles/2017/12/workflow-vs-script/){target="_blank"}.

[^extract1]: Please see the discussion in
[R for DataScience](http://r4ds.had.co.nz/tibbles.html#tibbles-vs.data.frame){target="_blank"} on how `tibble` objects differ from base `data.frame` objects in how the single bracket `[` is handled.
