---
title: "The Importance of Knowing What's Important"
linktitle: "Week 6: The Importance of Knowing What's Important"
output:
  blogdown::html_page:
    toc: true
menu:
  example:
    parent: Examples
    weight: 6
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

```{r load_packages, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Evaluation Phase
We are currently in the evaluation planning phase. This involves

```{r echo = FALSE}

unchecked <- as.character(fontawesome::fa("circle", fill = "#e4e4e4", height = "15px"))

checked <- as.character(fontawesome::fa("check-circle", fill = "#428bca", height = "15px"))

plan <- tibble(
  
  phase = c("Planning",
            ""),
  
  task = c("Discovering needs",
           "Suggesting a course of action"),
  
  current <- c(checked,
               unchecked)
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
  plan %>%
  kbl(escape = FALSE,
      align = 'llc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "20em") %>% 
  row_spec(2, extra_css = 'vertical-align: middle !important;') 
```
</center>

## More Logic Models

The [Division of Extension](https://fyi.extension.wisc.edu/programdevelopment/){target="_blank"} have a lot of resources covering program development and evaluation.

As you begin to think about a logic model, you need not stick the one provided. You can look around for others and one comprehensive resource is their repository of [logic models](https://fyi.extension.wisc.edu/programdevelopment/logic-models/){target="_blank"}. 
