---
title: "Making Sense and Interpreting Nonsense"
linktitle: "Week 7: Making Sense and Interpreting Nonsense"
output:
  blogdown::html_page:
    toc: true
menu:
  example:
    parent: Examples
    weight: 7
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

```{r load_packages, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Evaluation Phase
We are currently in the evaluation planning phase. This involves

```{r echo = FALSE}

unchecked <- as.character(fontawesome::fa("circle", fill = "#e4e4e4", height = "15px"))

checked <- as.character(fontawesome::fa("check-circle", fill = "#428bca", height = "15px"))

plan <- tibble(
  
  phase = c("Planning",
            ""),
  
  task = c("Discovering needs",
           "Suggesting a course of action"),
  
  current <- c(unchecked,
               checked)
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
  plan %>%
  kbl(escape = FALSE,
      align = 'llc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "20em") %>% 
  row_spec(2, extra_css = 'vertical-align: middle !important;') 
```
</center>

## More Needs Assessment

If you are interested in *needs assessments* or simply want more information, consider downloading the text [*A Guide to Assessing Needs*](https://openknowledge.worldbank.org/bitstream/handle/10986/2231/663920PUB0EPI00essing09780821388686.pdf?sequence=1&isAllowed=y){target="_blank"} written by Ryan Watkins, Maurya West Meiers and Yusra Laila Visser for the World Bank.

The authors provide a very detailed breakdown of needs assessments and how to conduct varying types of analyses. While in-depth quantitative or qualitative analyses of your needs assessment is likely the scope of this course, future highly structured approaches may warrant these methods. The text really does a good job of breaking what to do where and when.
