---
title: "The Basics"
linktitle: "Week 1: The Basics"
menu:
  readings:
    parent: Print
    weight: 1
type: docs
weight: 1
output:
  blogdown::html_page:
    toc: true
---

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(downloadthis)
library(here)
library(knitr)
library(kableExtra)
```

### Get Some Advice
First things first:
<br>
<br>
<iframe src="/videos/snoop_syllabus.mp4" width="320" height="480" frameBorder="0">Read the syllabus.</iframe>
<br>
<br>Far be it from us to disagree with Snoop, so you should probably go read the [syllabus](/syllabus/) as soon as possible! While you're there, take a look the other areas as well, in particular the  [readings](/readings/), [data camp](/datacamp/), [materials](/materials/), [tasks](/tasks/), [to do list](/due/), and [resources](/resources/) pages.

## Literature

### Download Digital Copies
Social networks aren't just about making pretty pictures^[although that is very important!], rather it is done to convey a great deal of logistical information in an efficient way. To get an idea of what networks are and why they are so important, please download and go through this weeks readings. 

```{r echo=FALSE}
slackico <- as.character("/logos/slack-ico.png{width=20px}")

readings <- tibble(
  
  paper <- c(
   "Borgatti, S.P., Mehra, A, Brass, D.J. & Labianca, G. (2009) Network Analysis in the Social Sciences, *Science, 323*(5916), 892-895.",
   "Scott, J. (2017) What is Social Network Analysis? *Social network analysis* (4th ed., pp. 1-8). Sage.",
    "Scott, J. (2017) The History of Social Network Analysis. *Social network analysis* (4th ed., pp. 11-37). Sage."
  ),
  
  post <- c("*nothing this week*",
            "*nothing this week*",
            "*nothing this week*"
            ),
  
  channel <- c(
    "*not applicable*",
    "*not applicable*",
    "*not applicable*"
    ),

  link <- c(
    "*none*",
    "*none*",
    "*none*"
  ),
  
  .name_repair = "minimal"
  
)
```

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "readings", "EDP693gWeek1Readings.zip"),
  output_name = "Week 1 Readings",
  button_label = "Download the Readings",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Postings 
Some readings require you to post to a channel on Slack. These are provided in a table like the one shown below. While you have readings for this week, there is nothing to post about.

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Reading", "Post About", "Slack Channel", "Link"), 
      "html", 
      escape = FALSE,
      align = 'llcc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "30em") %>%
  column_spec(3, width = "20em") %>%
  column_spec(4, width = "5em") %>%
  row_spec(0, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(2, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(3, extra_css = 'vertical-align: middle !important;') 
```
</center>
