---
title: "Does it Work and Why Does it Work?"
linktitle: "Week 1: Evaluations"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  readings:
    parent: Readings
    weight: 1
type: docs
weight: 1
---

`r blogdown::shortcode("aes-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

<style>
.videoContainer {
    height: 480px;
    width: 320px;   
    padding: 26px;
}
</style>

### Get Some Advice
<center>
<div class="videoContainer">
<video width="320" controls>
    <source src="/videos/snoop_syllabus.mp4" type="video/mp4">

I'm sorry but your browser doesn't support embedded videos. You can however <a href="/videos/snoop_syllabus.mp4">download it</a>.

</video>
</div>
</center>

### Review 

#### Website

Far be it from us to disagree with Snoop, so you should probably go read the [syllabus](/syllabus/) as soon as possible! Additionally look over the other areas on this site: [tasks](/tasks/), [trainings](/trainings/), [to do list](/due/), and [resources](/resources/) pages for this class.

#### Surveys Companion site

You can get additional examples and materials for the 4th edition of *Internet, Phone, Mail, and Mixed-Mode Surveys: The Tailored Design Method* by clicking [here](https://bcs.wiley.com/he-bcs/Books?action=index&bcsId=9087&itemId=1118456149)

### Read Some Text

```{r echo=FALSE}

document <- as.character(fa("file", fill = "#e86af0", height = "25px"))

book <- as.character(fa("book", fill = "#f06ab5", height = "25px"))

site <- as.character(fa("link", fill = "	#a56af0", height = "25px"))

review <- tibble(
  
  title <- c("<i>CDC's Introduction to Evaluation</i>",
             "<i>Sample Surveys in Our Electronic World</i>",
             "<i>Using Surveys</i>"
  ),
  
  section = c(NA,
              "Chapter 1",
              "Chapter 14"),
  
  link <- c(
    paste0("[",site,"]",
    "(https://www.cdc.gov/eval/guide/introduction/index.htm){target='_blank'}"
    ),
    paste0("[",book,"]",
    "(https://ebookcentral.proquest.com/lib/wvu/reader.action?docID=1762797&ppg=21){target='_blank'}"
    ),
    paste0("[",book,"]",
    "(https://ebookcentral.proquest.com/lib/wvu/reader.action?docID=2144898&ppg=361){target='_blank'}"
    )
    
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
review %>%
  mutate_all(replace_na,"") %>%
  kbl(col.names = c("Title", 
                    "Section",
                    "Link"), 
      "html", 
      escape = FALSE,
      align = 'llc') %>%
   kable_paper(full_width = TRUE) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "10em") %>% 
  row_spec(0:nrow(review), extra_css = 'vertical-align: middle !important;', color = "#f7f7f7", background = "transparent") 
```
</center>
