---
title: "Rethinking the Way You Think"
linktitle: "Week 2: Rethinking the Way You Think"
menu:
  content:
    parent: Readings
    weight: 1
type: docs
weight: 1
bibliography: "../../static/bib/references.bib"
csl: "../../static/bib/chicago-fullnote-bibliography-no-bib.csl"
output:
  blogdown::html_page:
    toc: true
---

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(downloadthis)
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
```

### Read Some Papers
For each reading below, write a *single* post on Slack with the following:

  - a reflection / reaction to the content *and*
  - a question about something specific
  
```{r echo=FALSE}

readings <- tibble(
  
  paper <- c("Davidson, J. (2007). Editorial: Unlearning some of our social scientist habits. *Journal of MultiDisciplinary Evaluation 4*(8). 3-6.", 
               "Mathison, S. (2006). What is the difference between evaluation and research - and why do we care? In N.L. Smith and P.R. Brandon (Eds.) *Fundamental issues in evaluation*. Guilford Press."
               ),
  
  post <- c(
    "[`#davidson`](https://2021edp617.slack.com/archives/C01KV12ELKC){target='_blank'}",
   "[`#mathison`](https://2021edp617.slack.com/archives/C01KV11R64S){target='_blank'}"                    
                       ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Reading", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em")
```
</center>

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "papers", "EDP612Week2Readings.zip"),
  output_name = "Week 2 Readings",
  button_label = "Download the Readings",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
  
#### Note about the posts 
**Remember this is a graduate level class and your writing should reflect that**. Moreover, these postings should be in APA 7th Edition formatting unless otherwise noted. The following general idea will be used when assessing your *initial posts*, but this is not a rubric. 

- ✔+: (*11.5 points in gradebook*) Posts are well defined responses that fully address and develop all aspects of the prompt such that they
  + advance the discussion, 
  + are factually correct, 
  + are cited correctly when necessary, *and*
  + provide a clear, concise, reflective and substantive contribution.
- ✔: (*10 points in gradebook*) Posts well defined responses that mostly address all aspects of the prompt such that they
  + generally advances the discussion, 
  + are factually correct, 
  + are cited correctly when necessary, *but*
  + lack clarity or full development of the concept(s). 
- ✔−: (*5 points in gradebook*) Posts responses that address some aspects of the prompt where responses are
  + not clear *or*
  + ill-prepared *or*
  + repetitive *or*
  + superficial *or*
  + unsubstantiated.
- ✘: (*0 points in gradebook*) Posts responses that are
  + non existent *or*
  + incorrect *or*
  + irrelevant to the discussion *or*
  + off-topic.

Otherwise *0 points (0%) in gradebook*.
