---
title: "Rethinking the Way You Think"
linktitle: "Week 2: Rethinking the Way You Think"
menu:
  content:
    parent: Readings
    weight: 2
type: docs
weight: 1
bibliography: "../../static/bib/references.bib"
csl: "../../static/bib/chicago-fullnote-bibliography-no-bib.csl"
output:
  blogdown::html_page:
    toc: true
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Read Some Papers
For each reading below, write a **single post** on Slack with the following:
  
  - a reflection / reaction to the content *and*
  - a question about something specific

```{r echo=FALSE}

readings <- tibble(
  
  paper <- c("Davidson, J. (2007). Editorial: Unlearning some of our social scientist habits. *Journal of MultiDisciplinary Evaluation 4*(8). 3-6.", 
             "Mathison, S. (2006). What is the difference between evaluation and research - and why do we care? In N.L. Smith and P.R. Brandon (Eds.) *Fundamental issues in evaluation*. Guilford Press."
  ),
  
  post <- c(
    "[`#davidson`](https://2021edp617.slack.com/archives/C01KV12ELKC){target='_blank'}",
    "[`#mathison`](https://2021edp617.slack.com/archives/C01KV11R64S){target='_blank'}"                    
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Reading", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em")
```
</center>
  
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "readings", "EDP617Week2Readings.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Week 1 Readings",
  button_label = "Download the Readings",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```


### Note about the posts 
**Remember this is a graduate level class and your writing should reflect that**. Moreover, these postings should be in APA 7th Edition formatting unless otherwise noted. The following general idea will be used when assessing your *initial posts*, but this is not a rubric. 

```{r echo=FALSE}

plus <- as.character(fa("plus", fill = "#5cb85c", height = "25px"))

check <- as.character(fa("check", fill = "#0275d8", height = "25px"))

minus <- as.character(fa("minus", fill = "#f0ad4e", height = "25px"))

not <- as.character(fa("exclamation", fill = "#d9534f", height = "25px"))

empty <- as.character(fa("times", fill = "#292b2c", height = "25px"))

initials <- tibble(
  
  range <- c(plus, 
             check,
             minus, 
             not,
             empty
  ),
  
  worth <- c("*11.5*",
             "*10*",
             "*5*",
             "*0*",
             "*0*"),
  
  criteria <- c(
    
    "Posts are well defined that fully address and develop all aspects of the prompt such that they

advance the discussion,<br>
are factually correct,<br>
are cited correctly when necessary, *and*<br>
provide a clear, concise, reflective and substantive contribution",

"Posts are mostly well defined that tend to address all aspects of the prompt such that they

generally advance the discussion,<br>
are factually correct,<br>
are cited correctly when applicable, *but*<br>
lack clarity or full development of the concept(s)",

"Posts are undertsandable but are not cohesive such that they do lack 

clarity *or*<br>
depth *or*<br>
non-repetitiveness *or*<br>
preparedness *or*<br>
justification",

"Posts are generally incoherant or superficial such that they are

repeated *or*<br>
incorrect *or*<br>
irrelevant *or*<br>
off-topic",

"Posts are nonexistent or lack merit"

  ),

.name_repair = "minimal"

)

```

<center>
```{r, echo=FALSE}
initials %>%
  kbl(
    col.names = c("Marker", "Point Value", "Criteria"), 
    "html", 
    escape = FALSE,
    align = 'ccl'
  ) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>% 
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  row_spec(0, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(2, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(3, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(4, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(5, extra_css = 'vertical-align: middle !important;') 
```
</center>