---
title: "Rethinking the Way You Think"
linktitle: "Week 2: Rethinking the Way You Think"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  readings:
    parent: Readings
    weight: 2
type: docs
weight: 1
---

`r blogdown::shortcode("aes-header")`

```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Read Some Papers
For each reading below, write a <b>single post</b> on Slack with the following:
  
  1. a reflection / reaction to the content <i>and</i>
  2. a question for the original author of the post about something specific

```{r echo=FALSE}

readings <- tibble(
  
  paper <- c("Davidson, J. (2007). Editorial: Unlearning some of our social scientist habits. <i>Journal of MultiDisciplinary Evaluation 4</i>(8). 3-6.", 
             "Mathison, S. (2006). What is the difference between evaluation and research - and why do we care? In N.L. Smith and P.R. Brandon (Eds.) <i>Fundamental issues in evaluation</i>. Guilford Press."
  ),
  
  post <- c(
    "<a https://2022edp617.slack.com/archives/C02UBC12PC5 target='_blank' style='color: #ff8384;'><font size='4px'>\\ #davidson</font></a>",
    "<a https://2022edp617.slack.com/archives/C02UEAF6135 target='_blank' style='color: #ff8384;'><font size='4px'>\\ #mathison</font></a>"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Reading", "Channel"), 
      format = "html", 
      escape = FALSE,
      align = 'lc') %>%
  kable_paper(full_width = F) %>%
  column_spec(1, width = "30em", color = "#ffffff", extra_css = 'vertical-align: middle !important;') %>%
  column_spec(2, width = "10em", color = "#ffffff", extra_css = 'vertical-align: middle !important;') %>% 
  row_spec(0:2, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent") 

```
</center>
  
<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "readings", "EDP617Week2Readings.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Week 1 Readings",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download the Readings</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
</center>

### Reminder

Please make sure to look over the [Writing on Slack](/tasks/#writing-on-slack) and [Responding on Slack](/tasks/#responding-on-slack) prior to posting.

