---
title: "The Basics"
linktitle: "Week 2: The Basics"
output:
  blogdown::html_page:
    toc: true
menu:
  readings:
    parent: Readings
    weight: 1
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Literature

### Download Digital Copies

```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "readings", "EDP611Week2Readings.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Week 2 Readings",
  button_label = "Download Readings",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Read Some Papers
There are no posts based on the readings this week.

```{r echo=FALSE}

slackico <- as.character("/readings/01-readings_files/slack-ico.png{width=20px}")


readings <- tibble(
  
  paper <- c(
    "Desjardins, C. D., & Bulut, O. (2018). Classical Test Theory. In *Handbook of educational measurement and psychometrics using R*. essay, CRC Press.",
   "Bardhoshi, G. & Erford, B.T. (2017) Processes and Procedures for Estimating Score Reliability and Precision, *Measurement and Evaluation in Counseling and Development, 50*, 4, 256-263.",
    "Tate, K.A., Bloom, M.L., Tassara, M.H. & Caperton, W. (2014) Counselor Competence, Performance Assessment, and Program Evaluation, *Measurement and Evaluation in
Counseling and Development, 4*, 291-306."
  ),
  
  post <- c("*none*",
            "*none*",
            "*none*"
            ),
  
  channel <- c(
    "*not applicable*",
    "*not applicable*",
    "*not applicable*"
    ),

  link <- c(
    "*none*",
    "*none*",
    "*none*"
  ),
  
  .name_repair = "minimal"
  
)

```


<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Reading", "Post", "Slack Channel", "Link"), 
      "html", 
      escape = FALSE,
      align = 'llcc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "30em") %>%
  column_spec(3, width = "20em") %>%
  column_spec(4, width = "5em") %>%
  row_spec(0, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(2, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(3, extra_css = 'vertical-align: middle !important;') 
```
</center>

### Review Some Materials

```{r echo=FALSE}

document <- as.character(fa("file", fill = "#e86af0", height = "20px"))

book <- as.character(fa("book", fill = "#f06ab5", height = "20px"))

site <- as.character(fa("link", fill = "	#a56af0", height = "20px"))

review <- tibble(
  
  source <- c("Part II: Quantitative Research Designs covering Chapters 5-6 in Balkin & Kleist",
              "Chapter II: Measurement, Scales, and Scoring in Albano"
  ),
  
  link <- c(
    paste0("[",site,"]",
    "(https://library.wvu.edu/){target='_blank'}"
    ),
    paste0("[",book,"]",
    "(https://www.thetaminusb.com/intro-measurement-r/measurement.html){target='_blank'}^[Again copy and paste the code into your R console to follow along and if you do not understand something please reach out.]"
    )
    
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
review %>%
  kbl(col.names = c("Review", "Link"), 
      "html", 
      escape = FALSE,
      align = 'lc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  row_spec(0, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1, extra_css = 'vertical-align: middle !important;')
```
</center>




