---
title: "Aims, Scope and Sequencing"
linktitle: "Week 3: Aims, Scope and Sequencing"
menu:
  content:
    parent: Readings
    weight: 3
type: docs
weight: 1
bibliography: "../../static/bib/references.bib"
csl: "../../static/bib/chicago-fullnote-bibliography-no-bib.csl"
output:
  blogdown::html_page:
    toc: true
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Read the Book

Please read

```{r echo=FALSE}

readings <- tibble(
  
  title <- c("What is Evaluation?", 
             "Defining the Purpose of Evaluation",
             "Identifying Evaluative Criteria"
  ),
  
  number <- c(
    "1",
    "2" ,
    "3"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Title", "Chapter"), 
      "html", 
      escape = FALSE,
      align = 'lc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em")
```
</center>
  
Then go through the [*Criterial and Interpretive Evaluation* slideshow](/lesson/03-lesson/#learning-about-criteria). Finally create a **single post** under [`#criteria`](https://2021edp617.slack.com/archives/C01M4PL1R5X){target='_blank'} that addresses the following

1. what general steps would you take to assess criteria for a program you have been selected to evaluate? and

2. question about something specific in any of the chapters. 

## Respond to Posts
Please create **two responses** for each of the posts below on Slack. 

- [`#davidson`](https://2021edp617.slack.com/archives/C01KV12ELKC){target='_blank'}

- [`#mathison`](https://2021edp617.slack.com/archives/C01KV11R64S){target='_blank'}

### Note about the responding to posts 
Your responses to postings should follow the same basic criteria outlined in the original post. Remember to use the `Reply in thread` option when replying! If you need a reminder on how to do this, please click [here](/lesson/02-lesson/#responses).

