---
title: "Causation and Criteria"
linktitle: "Week 4: Causation and Criteria"
menu:
  content:
    parent: Readings
    weight: 4
type: docs
weight: 1
bibliography: "../../static/bib/references.bib"
csl: "../../static/bib/chicago-fullnote-bibliography-no-bib.csl"
output:
  blogdown::html_page:
    toc: true
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Read the Book

Please read and address the following questions using a single post apiece

```{r echo=FALSE}

readings <- tibble(
  
  title <- c("Oragnizing the Criteria and Identifying Potential Sources of Evidence", 
             "Dealing With the Causation Issue"
  ),
  
  number <- c(
    "4",
    "5"
  ),
  
  question <- c(
    "Given a list of multiple criteria given to you by a sponsor or stakeholder prior to conducting an evaluation, how would you determine which are more important than others?",
    "Can we determine causality in every circustance?^[There is a stark division between the people who stand on one side of this issue or the other and you may be suprised to know that your response can often be used as a predictor for the type of evaluation you are likely to take given a choice.]"
  ),
  
  
  hastag <- c(
    "[#ranking-criteria](https://2021edp617.slack.com/archives/C01M9DLL6BG){target='_blank'}",
    "[#causality-conundrum](https://2021edp617.slack.com/archives/C01MURJ3909){target='_blank'}"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Title", "Chapter", "Question", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lcll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>%
  column_spec(4, width = "10em") 
```
</center>
  
## Respond to Posts
Please create **two responses** for the post below on Slack. 

- [`#criteria`](https://2021edp617.slack.com/archives/C01M4PL1R5X){target='_blank'}

### Note about the responding to posts 
Your responses to postings should follow the same basic criteria outlined in the original post. Remember to use the `Reply in thread` option when replying! If you need a reminder on how to do this, please click [here](/lesson/02-lesson/#responses).

