---
title: "The In-Crowd"
linktitle: "Week 5: The In-Crowd"
menu:
  readings:
    parent: Print
    weight: 5
type: docs
weight: 1
output:
  blogdown::html_page
---

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(tidyverse)
library(downloadthis)
library(here)
library(knitr)
library(kableExtra)
```

## Literature

Please download and go through this weeks reading which will help with this week's task that introduces *chord diagrams*. 

```{r echo=FALSE}
slackico <- as.character("/logos/slack-ico.png{width=20px}")

readings <- tibble(
  
  paper <- c(
   "Luke, D.A. (2015). Advanced Network Graphics. *A user's guide to network analysis in R* (1st ed., pp. 73-87). Springer. [10.1007/978-3-319-23883-8](http://dx.doi.org/10.1007/978-3-319-23883-8){target='_blank'}",
   "Ognyanova, K. (2021) Network visualization with R. Retrieved from [www.kateto.net/network-visualization](www.kateto.net/network-visualization){target='_blank'}"
  ),
  
  post <- c("*nothing this week*",
            "*nothing this week*"),
  
  channel <- c(
    "*not applicable*",
    "*not applicable*"
    ),

  link <- c(
    "*none*",
    "*none*"
  ),
  
  .name_repair = "minimal"
  
)
```

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "readings", "EDP693gWeek5Readings.zip"),
  output_name = "Week 5 Readings",
  button_label = "Download the Readings",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Postings 

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Reading", "Post About", "Slack Channel", "Link"), 
      "html", 
      escape = FALSE,
      align = 'llcc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "50em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "20em") %>%
  column_spec(4, width = "5em") %>%
  row_spec(0, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1, extra_css = 'vertical-align: middle !important;') %>%
  row_spec(2, extra_css = 'vertical-align: middle !important;') 
```
</center>
