---
title: "The Importance of Knowing What's Important"
linktitle: "Week 6: The Importance of Knowing What's Important"
menu:
  content:
    parent: Readings
    weight: 6
type: docs
weight: 1
bibliography: "../../static/bib/references.bib"
csl: "../../static/bib/chicago-fullnote-bibliography-no-bib.csl"
output:
  blogdown::html_page:
    toc: true
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
library(here)
```

## Read the Book

Please read and address the following questions using a single post

```{r echo=FALSE}

readings <- tibble(
  
  title <- c('Determining Importance',
             'The Merit Determination Step'
  ),
  
  number <- c(
    "7",
    "8"
  ),
  
  question <- c(
    "During your interview, how you would or have already assessed important criteria?",
    "What would you do in a situation where your view on aspects of an evaluation have merit but your sponsor does not. Remember that you as the evaluator are the expert *but* the sponsor is the person who hired you."
  ),
  
  
  hashtag <- c(
    "[#important-criteria](https://2021edp617.slack.com/messages/important-criteria){target='_blank'}",
    "[#merit-disagreement](https://2021edp617.slack.com/messages/merit-disagreement){target='_blank'}"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Title", "Chapter", "Question", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lcll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>%
  column_spec(4, width = "10em") 
```
</center>

<!--
## Read a Paper

```{r echo=FALSE}

papers <- tibble(
  
  title <- c('Valuing, Evaluation Methods, and the
Politicization of the Evaluation Process'
  ),
  
  Citation <- c(
    "Chelimsky (2012)"
  ),
  
  question <- c(
    "Assume that there is some level of politicization of the evaluative process in government. How egregious do you think this is? Provide some evidence in your narrative regarding  specific programs and how you currently see/ have seen this politicization in action."
  ),
  
  hashtag <- c(
    "[#evaluation-politicization](https://2021edp617.slack.com/messages/evaluation-politicization){target='_blank'}"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
papers %>%
  kbl(col.names = c("Title", "Chapter", "Question", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lcll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>%
  column_spec(4, width = "10em") 
```
</center>


```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "readings", "Chelimsky (2012).pdf")

downloadthis::download_file(
  path = loc,
  output_name = "Chelimsky (2012)",
  button_label = "Download the Paper",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
-->

## Respond to Posts
Please create **two responses** apiece for the post below on Slack. 

- [`#evaluation-politicization`](https://2021edp617.slack.com/messages/evaluation-politicization){target='_blank'}

- [`#which-values`](https://2021edp617.slack.com/messages/which-values){target='_blank'}

### Note about the responding to posts 
Your responses to postings should follow the same basic criteria outlined in the original post. Remember to use the `Reply in thread` option when replying! If you need a reminder on how to do this, please click [here](/lesson/02-lesson/#responses).

