---
title: "Making Sense and Interpreting Nonsense"
linktitle: "Week 7: Making Sense and Interpreting Nonsense"
menu:
  content:
    parent: Readings
    weight: 7
type: docs
weight: 1
bibliography: "../../static/bib/references.bib"
csl: "../../static/bib/chicago-fullnote-bibliography-no-bib.csl"
output:
  blogdown::html_page:
    toc: true
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
library(here)
```

## Read the Book

Please read and address the following questions using a single post for each chapter

```{r echo=FALSE}

readings <- tibble(
  
  title <- c('Synthesis Methodology',
             'Putting it All Together'
  ),
  
  number <- c(
    "9",
    "10"
  ),
  
  question <- c(
    "Do you agree with Davidson that a synthesis is necessary? Please explain your viewpoint.",
    "What parts of the KEC are needed in your evaluation? Why did you choose those in lieu of others?"
  ),
  
  
  hashtag <- c(
    "[#views-on-synthesis](https://2021edp617.slack.com/messages/views-on-synthesis){target='_blank'}",
    "[#including-kec-parts](https://2021edp617.slack.com/messages/including-kec-parts){target='_blank'}"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Title", "Chapter", "Question", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lcll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>%
  column_spec(4, width = "10em") 
```
</center>

## Read a Paper

The paper below is as theory based as the course will get but a theory-driven evaluation (TDE) has a great deal of practical applications.

```{r echo=FALSE}

papers <- tibble(
  
  title <- c('Theory Driven Evaluations'
  ),
  
  Citation <- c(
    "Chen  (2012)"
  ),
  
  question <- c(
    "What genersal steps are needed to ensure that a theory-driven evaluation occurs? How do these translate to your particular evaluation?"
  ),
  
  hashtag <- c(
    "[#tde](https://2021edp617.slack.com/messages/tde){target='_blank'}"
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
papers %>%
  kbl(col.names = c("Title", "Chapter", "Question", "Channel"), 
      "html", 
      escape = FALSE,
      align = 'lcll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>%
  column_spec(4, width = "10em") 
```
</center>


```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "readings", "Chen (2012).pdf")

downloadthis::download_file(
  path = loc,
  output_name = "Chen (2012)",
  button_label = "Download the Paper",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```


## Respond to Posts
Please create **two responses** apiece for the post below on Slack. 

- [`#important-criteria`](https://2021edp617.slack.com/messages/important-criteria){target='_blank'}

- [`#merit-disagreement`](https://2021edp617.slack.com/messages/merit-disagreement){target='_blank'}

### Note about the responding to posts 
Your responses to postings should follow the same basic criteria outlined in the original post. Remember to use the `Reply in thread` option when replying! If you need a reminder on how to do this, please click [here](/lesson/02-lesson/#responses).

