---
title: "Making Sense and Interpreting Nonsense"
linktitle: "Week 7: Making Sense and Interpreting Nonsense"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  readings:
    parent: Readings
    weight: 7
type: docs
weight: 1
---

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/5.15.4/css/all.min.css" />

<link href='https://fonts.googleapis.com/css?family=Roboto Condensed' rel='stylesheet'>

<style>
.hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0px;
  left: 0px;
  right: 0px;
  bottom: 0px;
  border-radius: 5px;
  background: #9f54fb;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover:before, 
.hvr-sweep-to-left:focus:before, 
.hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}

iframe {
  border: none;
}

td, th, tr, table {
    border: 0 !important;
    border-spacing:0 !important;
  }
  
.box{
    float:left;
    margin-right:10%;
}

.clear{
    clear:both;
}

.wrapper{
  display:inline-flex;
}.wrapper .icon{
  margin: 0 20px;
  cursor:pointer;
  display:flex;
  align-items:center;
  justify-content:center;
  flex-direction:column;
  position: relative;
  z-index:2;}.wrapper .icon span{
  position:relative;
  z-index:2;
  height: 60px;
  width: 60px;
  display:block;
  background: #282A35;
  box-shadow: 0px 0px 0px 0px rgba(0,0,0,0.1);
  border-radius:50%;
  text-align:center;
  transition: all 0.4s cubic-bezier(0.68, -0.55, 0.265, 1.55);
}.wrapper .icon span i{
  font-size:20px;
  line-height:60px;
}.wrapper .icon .tooltip{
  position:absolute;
  top:0px;
  background: #282A35;
  box-shadow: 0px 0px 0px 0px rgba(0,0,0,0.1);
  font-size: 20px;
  font-family: 'Roboto Condensed';
  padding: 10px 30px;
  border-radius: 25px;
  color:white;
  opacity:0;
  pointer-events: none;
  transition: all 0.4s cubic-bezier(0.68, -0.55, 0.265, 1.55);
}.wrapper .icon:hover .tooltip{
  opacity:1;
  pointer-events: auto;
  top:-91px;
}.wrapper .icon .tooltip:before{
  position:absolute;
  content:"";
  height:15px;
  width:15px;
  bottom:-8px;
  left:50%;
  transform: translateX(-50%) rotate(45deg);
}.wrapper .icon:hover span,
.wrapp .icon:hover .tooltip{
  text-shadow: 0px -1px 0px rgba(0,0,0,0.4);
}.wrapper .icon:hover span{
  color: #fff;
}.wrapper .leftright:hover span,
.wrapper .leftright:hover .tooltip,
.wrapper .leftright:hover .tooltip:before{
  background:#1b85b8;
}.wrapper .info:hover span,
.wrapper .info:hover .tooltip,
.wrapper .info:hover .tooltip:before{
  background:#559e83;
}.wrapper .github:hover span,
.wrapper .github:hover .tooltip,
.wrapper .github:hover .tooltip:before{
  background:#9e5570;
}.wrapper .youtube:hover span,
.wrapper .youtube:hover .tooltip,
.wrapper .youtube:hover .tooltip:before{
  background:#55959e;
}

i.fa.fa-save{
color:#ffffff;
}
</style>

<script>
$(document).ready(function(){
     $('[data-toggle="tooltip"]').tooltip();   
});
</script>

```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
library(here)
library(showtext)
font_add("arnar",
    regular = "Arial Narrow.ttf",
    bold = "Arial Narrow Bold.ttf")
```

## Respond to Posts

Please create **two responses** for each of the posts below on 

- <font face="Arial Narrow" size="4px">[`#important-criteria`{=html}](https://2022edp617.slack.com/archives/C032T8GK5EZ){target='_blank'}</font>

- <font face="Arial Narrow" size="4px">[`#merit-disagreement`{=html}](https://2022edp617.slack.com/archives/C032FH7QLRM){target='_blank'}</font>

## Read the Book

Please read and address the following questions using a single post for each chapter

```{r echo=FALSE}

readings <- tibble(
  
  title <- c('<i>Synthesis Methodology</i>',
             '<i>Putting it All Together</i>'
  ),
  
  chapter <- c(
    "9",
    "10"
  ),
  
  arrow = c("external",
            "external"),
  
  link = c(
    "https://methods-sagepub-com.wvu.idm.oclc.org/book/evaluation-methodology-basics/n9.xml",
    "https://methods-sagepub-com.wvu.idm.oclc.org/book/evaluation-methodology-basics/n10.xml"),
  
  question <- c(
    "Do you agree with Davidson that a synthesis is necessary? Please explain your viewpoint.",
    "What parts of the KEC are needed in your evaluation? Why did you choose those in lieu of others?"
  ),
  
  area = c("`#views-on-synthesis`{=markdown}",
            "`#including-kec-parts`{=markdown}"),
  
  post = c(
    "https://2022edp617.slack.com/archives/C0346A5MQFP",
    "https://2022edp617.slack.com/archives/C0342HMFXB8"
  ),

  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  mutate(arrow = case_when(
    str_detect(`arrow`, "external") ~ '<div style="font-size: 0.5rem;"><i class="fa fa-external-link fa-2x" aria-hidden="true" style="color:#559977"></i></div>',
    TRUE ~ NA_character_
  )
  ) %>%
  mutate(link = na_if(link, "")) %>%
  mutate(link = case_when(
    !is.na(arrow) ~ paste0("<a href=",link," target='_blank'>",arrow,"</a>"),
    TRUE ~ NA_character_
  )
  ) %>%
  mutate(post = case_when(
    !is.na(area) ~ paste0("<a href=",post," target='_blank'>",area,"</a>"),
    TRUE ~ NA_character_
  )
  ) %>%
  select(-arrow, -area) %>% 
  mutate_all(replace_na,"") %>%
  kbl(col.names = c("Title", "Chapter", "Link", "Question", "Post"), 
      "html", 
      escape = FALSE,
      align = 'lcclc') %>%
  kable_paper(full_width = F) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "10em") %>% 
  row_spec(0:2, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent") 
```
</center>

## Read a Paper

The paper below is as theory based as the course will get. Given that a theory-driven evaluation (TDE) has a great deal of practical applications especially in reference to a logic model. Please read and address the following question using a single post

```{r echo=FALSE}

paper <- tibble(
  
  title = c('<i>Theory Driven Evaluations</i>'),

chapter = c("Chen (2012)"),

arrow = c("external"),

question = c("What general steps are needed to ensure that a theory-driven evaluation occurs? How do these translate to your particular evaluation?"),
             
area = c("`#tde`{=markdown}"),

post = c(
  "https://2022edp617.slack.com/archives/C033UKWRQB1"
),

.name_repair = "minimal"

)

```

<center>
```{r, echo=FALSE}
paper %>%
  mutate(arrow = case_when(
    str_detect(`arrow`, "external") ~ '<div style="font-size: 0.5rem;"><i class="fa fa-external-link fa-2x" aria-hidden="true" style="color:#559977"></i></div>',
    TRUE ~ NA_character_
  )
  ) %>%
  mutate(post = case_when(
    !is.na(area) ~ paste0("<a href=",post," target='_blank'>",area,"</a>"),
    TRUE ~ NA_character_
  )
  ) %>%
  select(-arrow, -area) %>% 
  mutate_all(replace_na,"") %>%
  kbl(col.names = c("Title", "Chapter", "Question", "Post"), 
      "html", 
      escape = FALSE,
      align = 'lclc') %>%
  kable_paper(full_width = F) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em") %>% 
  column_spec(4, width = "10em") %>% 
  row_spec(0:1, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent") 
```
</center>
  
  <center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "readings", "Chen (2012).pdf")

downloadthis::download_file(
  path = loc,
  output_name = "Chen (2012)",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download the Paper",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
)
```
</center>

