---
title: "The Chi Square Test and Measures of Association"
linktitle: "Week 12: The Chi Square Test and Measures of Association"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  readings:
    parent: Readings
    weight: 12
type: docs
weight: 1
---

## Text 

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
```

`r blogdown::shortcode("aes-header")`


```{r eval = TRUE, echo = FALSE, message=FALSE}

read_schedule <- read_csv("read.csv",
                          show_col_types = FALSE) %>% 
                  as_tibble() %>%
                  mutate(Required = case_when(
                  Required == "checked" ~ as.character(fontawesome::fa("circle-check", fill = "#428bca", height = "15px")),
                Required == "unchecked" ~ as.character(fontawesome::fa("circle-xmark", fill = "#d9534f", height = "15px"))
              )) %>%
                  mutate(across(everything(), as.character)) %>%
                    filter(Group == 12) %>% #CHANGE HERE
                    select(-Group, -Details) %>%
                  filter_all(any_vars(!is.na(.))) %>% 
                  mutate(
                    across(everything(), ~replace_na(.x, ""))
                  ) %>%
                select_if(~!all(is.na(.))) %>%
  mutate(Title = paste0("<b>", Title, "</b>"))
  
```

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(read_schedule, 
      escape = FALSE,
      align = 'cllccccc') %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "10em") %>%
  column_spec(6, width = "10em") %>%
  column_spec(7, width = "10em") %>%
  row_spec(0:nrow(read_schedule), extra_css = 'vertical-align: middle !important;', background = "#212121", color = "#ffffff")
```

## Article

Please download and read [*Do Colleges Get What They Pay For? Evidence on Football Coach Pay and Team Performance*](/handouts/Colbert&Woodrow2015) by Colbert & Eckard (2015). You may not be familiar with all of the statistical measures, but pay special attention to the term ***regression to the mean*** and think abiut what it means in context and generally speaking. We'll be introducing this topic next week in class.
