---
title: " Theory and Terminology"
subtitle: "EDP 612 Week 1"
author: "Dr. Abhik Roy"
output: 
 xaringan::moon_reader:
   css: ['xaringan-themer.css', 'custom.css']
   nature:
     ratio: 16:9
     highlightStyle: github
     highlightLines: true
     countIncrementalSlides: false
     navigation:
         scroll: false
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.6.0/jquery.min.js"></script>

<script type="text/x-mathjax-config">
MathJax.Hub.Register.StartupHook("TeX Jax Ready",function () {
  MathJax.Hub.Insert(MathJax.InputJax.TeX.Definitions.macros,{
    cancel: ["Extension","cancel"],
    bcancel: ["Extension","cancel"],
    xcancel: ["Extension","cancel"],
    cancelto: ["Extension","cancel"]
  });
});
</script>

<style>
section {
    display: flex;
    display: -webkit-flex;
}

section p {
    margin: auto;
}

section {
    height: 600px;
    width: 60%;
    margin: auto;
    border-radius: 20px;
    background-color: #212121;
}

section p {
    text-align: center;
    font-size: 30px;
    background-color: #212121;
    border-radius: 20px;
    font-family: Roboto Condensed;
    font-style: bold;
    padding: 15px;
    color: #bff4ee;
}

#center {

text-align: center;

}

.center p {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

#center {

text-align: center;

}

</style>

```{css echo=FALSE}
.highlight-last-item > ul > li,
.highlight-last-item > ol > li {
  opacity: 0.5;
}
.highlight-last-item > ul > li:last-of-type,
.highlight-last-item > ol > li:last-of-type {
  opacity: 1;
}
```

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
library(here)
library(DT)
library(scales)
library(latex2exp)
library(showtext)
font_add_google("Roboto Condensed", "roboto")
showtext_auto()
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#bff4ee",
  table_row_border_color = "#212121",
  table_row_even_background_color = "#212121",
  footnote_font_size = "0.6em",
  header_font_google = xaringanthemer::google_font("Roboto Condensed", "700"),
  text_font_google   = xaringanthemer::google_font("Roboto Condensed", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", 
                                    "animate_css", 
                                    "tachyons"))

xaringanExtra::use_logo(
  image_url = here::here("static", "img", "course_hex.png"),
  link_url = "https://edp612.asocialdatascientist.com",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
)

```

# Promises...promises

--

The material here is dense

--

There is philosophy

--

This is the only day that it will be like this

---

# Nature of Educational Research

Four types of knowledge yielded by educational research

<br>
<br>
.pull-left[
<p id="center" style="color:#91b8ff; font-weight: bold; border:1px; border-style:solid; border-color:#91b8ff; border-radius: 25px; padding: 0.3em;">
Descriptive
</p>
]

--

.pull-right[
<p id="center" style="color:#ff91b8; font-weight: bold; border:1px; border-style:solid; border-color:#ff91b8; border-radius: 25px; padding: 0.3em;">
Predictive
</p>
]

--

.pull-left[
<p id="center" style="color:#91efff; font-weight: bold; border:1px; border-style:solid; border-color:#91efff; border-radius: 25px; padding: 0.3em;">
Improvement
</p>
]

--

.pull-right[
<p id="center" style="color:#ffd891; font-weight: bold; border:1px; border-style:solid; border-color:#ffd891; border-radius: 25px; padding: 0.3em;">
Explanative
</p>
]

---

# <span style="color:#91b8ff"> Descriptive</span> Studies

--

- Describe natural or social phenomena

  >- To identify areas for further research

--

  >- To help in planning resource allocation (aka needs assessment)

--

  >- Provide informational information about a condition or disease
  
--

- Dependent upon instrumentation for measurement and observation

--

<br>
<hr>

--

<br>
<i>Example</i> 
<br><br>
Study of 5 homosexual males who developed a rare pneumonia. This case report study led to the eventual discovery of HIV

---

# <span style="color:#ff91b8"> Predictive</span> Studies

--

- Predict a phenomena that will occur at a certain time from information available at an earlier time

--

<br>
<hr>

--

<br>
<i>Example</i> 
<br><br>
Scholastic Aptitude Test (SAT) scores are used to predict college freshmen grade point averages

---

# <span style="color:#91efff"> Improvement</span> Studies

--

- Concern the effectiveness of practices and interventions designed to improve practice

--

- Not really its own type of study

--

<br>
<hr>

--

<br>
<i>Example</i> 
<br><br>
Secondary schools that run all year improve knowledge retention

---

# <span style="color:#ffd891"> Explanative</span> Studies

--

- Explains a phenomenon


--

<br>
<hr>

--

<br>
<i>Example</i> 
<br><br>
Study habits change due to drinking behavior in college

---
 
# Activity

Working in groups of two or three, determine each study’s purpose

---

# Theory (Formal Definition)

--

- Explanation of a certain set of observed phenomena in terms of a system of constructs and laws that relate these constructs to each other

--

  >- Specifies relations between theoretical constructs
  
--

  >- Describes relations between constructs and measures

--

- System consists of a set of constructs and their relation to each other

---

# Theory (Informal Definition)

--

- General or overarching ideas that describe something

---

# Elements of Theory

--

- Theoretical construct

--

  >- <i>Constitutively defined construct</i>: having the power to establish existence.

--

  >- <i>Operationally defined construct</i>: having the power to define process(es)

--

- Variable

--

- Law

---

# Construct (Formal)

--

- Theoretical construct is a concept that is inferred from observed phenomena, defined constitutively or operationally

--

  >- <i>Constitutively defined construct</i>: Defined by referring to another construct
  
--

  >- <i>Operationally defined construct</i>: Defined by specifying the activities used to measure or manipulate it


---

# Construct (Informal)

- A way of bringing theory down to earth, helping to explain the different components of theories, as well as measure/observe their behavior.

--

<br>
<hr>

--

<br>
<i>Examples</i> 
<br><br>

- Ideas defined by poverty, trust, social justice, marriage, etc.

- People defined by race, ethnicity, age, etc.

---

# Variable (Formal)

--

- Quantitative or qualitative expression of a construct.

---

# Variable (Informal)

- A characteristic that differs from others.

--

<br>
<hr>

--

<br>
<i>Examples</i> 
<br><br>

- <i>Qualitative</i>: Suit on a deck of cards (Spades, Hearts, Diamonds, Clubs)


- <i>Quantitative</i>People defined by race, ethnicity, age, etc.

---

# Law

- Generalization about the causal, sequential, or other relationship between two or more constructs

--

<br>
<hr>

--

<br>
<i>Example</i> 
<br><br>

---

- <i>Logic</i>: If this then that

---

# Uses of Theory

--

- Theoretical constructs identify commonalities

--

- Laws of a theory enables one to predict and control phenomena

---

# Approaches to Theory Development

--

- Grounded theory approach

  >- Deriving constructs and laws directly from data collected

--

- Theory testing

  >- Formulating theory and then test the theory by collecting data
  
---

# Steps in Testing Theory

--

>- Formulate a hypothesis

>- Deduct observable consequences of the hypothesis

>- Test the hypothesis by making observations

---

# Application of Research to Educational Practice

--

- Improveing society and individual lives

--

- Developing tests
  >- Academic achievement
  >- Aptitudes
  >- Interests
  >- School-related personality characteristics

--

- No Child Left Behind Act

--

- [Institute of Education Sciences What Works Clearinghouse](https://ies.ed.gov/ncee/wwc/)


---

# Research Knowledgevs. Research Practice

--

<center>
<b><i>is</i></b> vs. <b><i>ought</i></b>
</center>

.pull-left[
Questions involving <b><i>is</i></b> can be answered objectively
]

.pull-right[
Questions involving <b><i>is</i></b> are value laden and only can be resolved through dialogue and a decision-making process
]

---

# Limitations of Research Knowledge

--

- Findings have limited generalizability

--

- Determines <b><i>is</i></b> but within a certain worldview and set of values

--

- Cannot be sole base for professional practice

---

# Importance of Basic Research

--

Even when this is not its purpose and even when practitioners are unaware of the research, research can influence practice

---

# Funding for Educational Research

Of Federal funding for public schools, less than 1% allocated for research annually between 1975 and 2003

---

# Activity

Parts of a manuscript

---

# Epistemology

--

- Branch of philosophy that studies the nature of knowledge and the process by which knowledge is acquired and validated

--

- Philosophers of science study nature of inquiry and knowledge in the natural and social sciences

--

- Variety of world views

---

# Positivism

--

- Assumes <i>objective reality</i> where physical and social reality is independent of those who observe it

--

- Observations of this independent reality, if unbiased, constitute scientific knowledge

--

- Focus on the study of observable behavior as the basis for building scientific knowledge

---

# Positivism

--

- Assumes <i>objective reality</i> that can only be known imperfectly

--

- Theories about objective reality cannot be validated in an absolute sense, but their validity can be strengthened through their resistance to research efforts to refute them

---

# Postpositivism: Research Practice

--

- Creates concepts and procedures that are shared and publicly accessible

--

- Replicability of findings

--

- Refutability of knowledge claims

--

- Controls for errors and biases

--

- Boundedness of knowledge claims

--

- Moral commitment to progressive discourse

---

# Constructivism

--

- Assumes <i>social reality</i>  is constructed by the individuals who participate in it where ascription of meanings are reliant on the social environment

--

- Each person constructs a self

--

- <i>Reflexivity<i>: researcher’s self is an integral constructor of the social reality

--

- Reflexivity – researcher’s self is an integral constructor of the social reality

---

# Modernism

--

- Promotes the advancement of knowledge through scientific observation

--

- Believes that “…under the seeming surface chaos of the world, of society, there exists a rationality, a basic truth that can be identified and harnessed for human good”

---

# Postmodernism

--

- Questions the rationality of human judgment

--

- Doubts that any method or theory, discourse or genre, tradition or novelty is “right” or better than another

---

# Realism

--

- Believes real world consists of layers of causal structures, some of them hidden from view, that interact to produce effects that may or may not be observable

---

Analytic Induction vs. Deduction

.pull-left[
<b><i>Induction</i></b>: Researcher analyzes the data and then infers findings
]

--

.pull-right[
<b><i>Deduction</i></b>: Researcher identifies findings prior to data collection and then searches for instances of findings
]

---

# Views of Causation

--

- Positivists:

  >- mechanical view of causation

--

  >- every step from cause can be traced to the effect
  
--

- Constructivists 

  >- interpretive view of causation
  
--

  >- people develop interpretations of the social environment that affect their subsequent action
  
--

- Realists 

  >- structural view of causation
  
--

  >- multiple layers of causal structures, which are real objects that interact with each other to cause people to take certain actions or, in some cases, to take no action. 

---

# <span style="color:#428bca">Quantitative</span> Research

--

- Assumes an objective social reality (positivist)

--

- Assumes that social reality is relatively constant across time and place

--

- Views causal relationships among social phenomena from a mechanistic perspective

--

- Takes a objective, detached stance toward research participants and their settings

--

- Studies populations or samples that represent populations

--

- Studies behavior and other observable phenomena

---

# <span style="color:#d9534f">Qualitative</span> Research

--

- Studies human actions in natural settings

--

- Makes holistic observations of the total context within which social action occurs

--

- Discovers concepts and theories after data have been collected

--

- Generates verbal and pictorial data to represent the social environment

--

- Uses analytic induction to analyze data

--

- Generalizes case findings by identifying other similar cases

--

- Prepares interpretive reports that reflect researchers’ constructions of the data and an awareness that readers will form their own constructions from what is reported

---

# Mixed Method Research

--

- Combines both quantitative and qualitative methods in a single study

--

- Not enough just to have both, they have to be <i>mixed</i> somehow!


---

# Formal Research Definition

--

A form of inquiry in which

--

1. Key concepts and procedures are carefully defined in such a way that inquiry can be replicated and possibly refuted

--

2. Controls are in place to minimize error and bias

--

3. Generalizability limits of the study are made explicit

--

4. Results of the study are interpreted in terms of what they contribute to the cumulative body of knowledge about the object of inquiry

---

# Scientific Research

--

Six guiding principles

--

1. Poses significant questions that can be investigated empirically

--

2. Links research to relevant theory and continually generates and refines theories

--

3. Uses methods that permit direct investigation of the questions

--

4. Provides a coherent and explicit chain of reasoning from an investigation’s empirical results to inferences based on these results

--

5. Calls for replication studies to validate, generalize, and synthesize the results of individual studies

--

6. Discloses a study’s findings to encourage professional scrutiny and critique

---

## That's it. Questions?