---
title: "Actually Evaluating Interventions"
linktitle: "Week 6: Actually Evaluating Interventions "
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  trainings:
    parent: Walkthroughs
    weight: 6
type: docs
weight: 2
---

`r blogdown::shortcode("r-walkthrough-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

# Sentiment Analysis

## Materials

The following download contains files that are provided to help you to understand and/or complete the walkthrough

<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "data", "EDP619Week6Walkthrough.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Week 6 Walkthrough",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

</center>

## Prepping

1. Open `Text-Mining-with-R-CH1&2-install.R` and run the syntax to install the packages you will need for this task. If you are asked to update any packages, please select `1: All`. If further requests come up to install additional components or files, please select `Yes`^[Should you have any issues with the installation, please reach out as soon as possible]

2. Open `Text-Mining-with-R-CH1&2-script.R` and run everything in it before starting. Use this script to copy and paste code from the chapters outlined below

## Tidy Text Mining

Follow the chapters

<ol>
  <li>
  <a href="https://www.tidytextmining.com/tidytext.html#tidytext">The tidy text format</a>
  </li>
  <li>
  <a href="https://www.tidytextmining.com/sentiment.html#sentiment">Sentiment analysis with tidy data</a>
  </li>
</ol> 

in *Text Mining with R: A Tidy Approach* by copying, pasting, and running the syntax in `Text-Mining-with-R-CH1&2-script.R` within RStudio. Please pay close attention to what is occurring and how the text data is being interpreted. We're going to have a work next week so please bring your laptops!
  
