---
title: "Actually Evaluating Interventions"
linktitle: "Week 6: Actually Evaluating Interventions "
output:
  rmarkdown::html_document:
    toc: true
menu:
  trainings:
    parent: Walkthroughs
    weight: 6
type: docs
weight: 2
---

`r blogdown::shortcode("r-walkthrough-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

# Sentiment Analysis

1. Download the following install script and run it in RStudio

<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "data", "EDP619Week6Walkthrough.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Week 6 Walkthrough",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

</center>


2. Follow chapters

  + [1: The tidy text format](https://www.tidytextmining.com/tidytext.html#tidytext)
  
  + [2: Sentiment analysis with tidy data](https://www.tidytextmining.com/sentiment.html#sentiment) 
  <br>
  <br>
  in *Text Mining with R: A Tidy Approach* by copying, pasting, and running the syntax. Please pay close attention to what is occurring and how the text data is being interpreted. We're going to have a work next week so please bring your laptops!
  
