---
title: "Comparing Groups"
linktitle: "Week 11: Bivariate Tables"
author: "Week 11"
output: 
 xaringan::moon_reader:
   css: xaringan-themer.css
---

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
library(patchwork)
library(compareGroups)
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#fcbb86",
  text_bold_color = "#fc868c",
   code_inline_color = "#86c7fc",
  header_font_google = xaringanthemer::google_font("Jost", "600"),
  text_font_google   = xaringanthemer::google_font("Jost", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
```

# Packages needed and a Note about Icons

Please load up the following packages. Remember to first install the ones you don't have.
```{r echo = FALSE, eval = TRUE, message=FALSE}
library(tidyverse)
library(compareGroups)
``` 

```{r echo = FALSE, eval = TRUE, message=FALSE}
suppressMessages(library(tidyverse))
suppressMessages(library(compareGroups))
``` 
<br>
<br>
You may come across the following icons. The table below lists what each means.
```{r eval = TRUE, echo = FALSE, purl=FALSE}
forward <- as.character(fontawesome::fa("forward", fill = "
#4682b4"))

stop <- as.character(fontawesome::fa("stop", fill = "#ff6347"))

link <- as.character(fontawesome::fa("link", fill = "#5cb85c"))

bookmark <- as.character(fontawesome::fa("bookmark", fill = "#5cb85c"))


icon_desc <- tibble(
  
  Icon = c(forward,
           stop, 
           link,
           bookmark),
  
  Description = c("Indicates that an example continues on the following slide.",
                  "Indicates that a section using common syntax has ended.",
                  "Indicates that there is an active hyperlink on the slide.",
                  "Indicates that a section covering a concept has ended.")
  
)
```

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, purl=FALSE}
kable(icon_desc, 
      escape = FALSE,
      align = 'cl') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "40em") %>%
  row_spec(0, background = "#181818") %>%
  row_spec(1, background = "#181818") %>%
  row_spec(2, background = "#181818") %>%
  row_spec(3, background = "#181818") %>%
  row_spec(4, background = "#181818") 
```

---

# The `compareGroups` package

- Originally designed to read, interpret, summarize, display and analyze epidemiological data. 

--

- Allows you to create everything from data summaries for quality control.

---

# Starting up

Let's use one of the preloaded data sets: `PREDIMED`.

>- longitudinal study containing several baseline characteristics of the participants as well as events occurred during the 7 years follow-up period given by variables `event` and `toevent`.

>-Each individual has been assigned to a three intervention diet randomly given by the variable `group`.

---


## Thats it!
