---
title: "Tidy and Other Related Open Source Texts"
menu:
  resources:
    parent: Guides
output:
  rmarkdown::html_document:
    toc: true
type: docs
weight: 7
---

`r blogdown::shortcode("r-walkthrough-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(widgetframe_self_contained = TRUE) 
knitr::opts_knit$set(root.dir = getwd())
```

<style>

table {
  padding: 50px;
  overflow: hidden;
  position: relative;
  display: inline-block;
  vertical-align: top;
  margin: 1.0em;
}

table:hover {
  overflow: visible;
}

td {
  width: 50px;
  position:relative;
}

img {
  -webkit-transition: all 0.5s linear;
          transition: all 0.5s linear;
  -webkit-transform: scale3d(1, 1, 1);
          transform: scale3d(1, 1, 1);
}

td:hover img {
  -webkit-transform: scale3d(1.2, 1.2, 1);
          transform: scale3d(1.2, 1.2, 1);
  transform: scale(2.0);
  transition: all .5s ease-in-out;
  position: absolute; 
  display: block; 
  z-index: 99;
  top: 35%;
  bottom: 55%;
  left: 35%;
  right: 35%;
  width: 100%;
  height: auto;
}

</style>

```{r functions, echo=FALSE}
max_nontrivial_divisor <- 
    function(x) {
      tryCatch({
        tibble(divisors = NA_integer_) %>%
          mutate(
            divisors = 
              case_when(
                numbers::isPrime(x) == TRUE ~ as.integer(1),
                numbers::isPrime(x) == FALSE ~ 
                  numbers::divisors(x) |>
                  as_tibble_col() |>
                  filter(!value == 1 & !value == x) |>
                  slice(which.max(value)) |>
                  pull() 
              ) 
            ) 
        }, 
      error=function(e) as.integer(1))
    }
```

<br>
```{=html}
<center>
<div class="wrapper">
    <div class="icon leftright">
      <div class="tooltip"><span style=width:200px;>Hover over any title to zoom in</span></div>
      <span><i class="fa-solid fa-expand"></i></span></div>
    <div class="icon info">
      <div class="tooltip"><span style=width:200px;>Click on any cover for the entire text</span></div>
      <span><i class="fa-solid fa-arrow-pointer"></i></span></div>
</div>
<br>
<hr style="width:20%">
</center>
```


```{r opttextstibble, echo=FALSE,warning=FALSE,message=FALSE}

opensourcetexts <-
  read_csv(here::here("content", "ost.csv"),
           show_col_types = FALSE) %>% 
  as_tibble() %>%
  arrange(title) %>%
  mutate(source = paste0(authors," (",year,"). <i>",title,"</i>."," (",edition," ed.) ",publisher,".")) %>%
  mutate(space = " ") %>%
  mutate(imglink = paste0("<a href='",link,"' target='_blank'> <img src='",loc,img,".",ftype,"' alt='",alt,"'></a>")) %>%
  select(imglink) %>%
  mutate(id = 1:nrow(.)%%(max_nontrivial_divisor(nrow(.)) %>% pull())) %>%
  pivot_wider(names_from = id,
              values_from = imglink) %>%
  unnest(col = everything())
  
```

<center>
```{r, echo=FALSE,warning=FALSE,message=FALSE}
opensourcetexts %>%
  kbl(col.names = NULL,
      format = "html", 
      escape = FALSE,
      align = 'c') %>%
  column_spec(1:ncol(opensourcetexts),
              width = "10em", 
              extra_css = 'vertical-align: middle !important;') %>%
  row_spec(1:nrow(opensourcetexts),
           extra_css = 'vertical-align: middle !important;',
           color = "#f7f7f7", 
           background = "transparent") %>%
  kable_styling()
```
</center>

This list only shows a very narrow slice of what are known as modern, or tidy friendly texts that are also in print. Barring a few instances here and there, each title should be accessible to anyone who understands the basic principles of *pipes* and *layers*. If you prefer a more comprehensive and up-to-date repository of nearly all open source texts about R, make sure to visit the impressive and ever growing [Big Book of R](https://www.bigbookofr.com/)! If you feel like I missed a helpful modern open source text, please let me know and I'll be happy to add it.

hello