---
title: "Create a Draft "
linktitle: "Week 4: Create a Draft "
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  tasks:
    parent: Deliverables
    weight: 1
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

`r blogdown::shortcode("aes-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

<style>
ul {
    margin-left: 1.5em
}
</style>


This task involves a multi-step process to address the underlying research or evaluation question of your eventual survey. Please follow the directions below^[These items assume that Qualtrics is used. If you are using another mode, please amend your responses to for the requirements of that platform]

1. First download the following 

<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "files", "skeleton.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Survey Skeleton",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
</center>
<br>

2. Open both files and review the variable names and descriptions in the codebook

3. Fill out the following columns^[While not required at the current time, you are free to fill out any of the remaining columns as needed]

  + **Item**. Survey items in the order they will currently appear. 
  
  + **ItemType**. Question type as allowed by [Qualtrics](https://www.qualtrics.com/support/survey-platform/survey-module/editing-questions/question-types-guide/question-types-overview/)
  
  + **Measure**. Direct measure of the item
  
  + **Latent**. Indirect measure of a category

4. After you have completed the draft, login to the [WVU Qualtrics](https://wvu.qualtrics.com) page, create a new survey, and construct an instrument that is a direct reflection of the skeleton

5. Share your survey by enabling [Collaboration](https://www.qualtrics.com/support/survey-platform/my-projects/sharing-a-project/)^[Please disallow editing privileges] 

6. Fill out the **Index** column with the item number provided in Qualtrics. Consider [auto-numbering](https://www.qualtrics.com/support/survey-platform/survey-module/survey-tools/auto-number-questions/) your questions to renumber them in order

7. Rename the document by following the [submission guidelines](/tasks/#submission-formatting) and submit this document to <a target="_blank" href="https://ecampus.wvu.edu/">eCampus</a><br><br>

<center>
<p id="rounded_corners">
All incremental deliverables can be found on the main <a href="/tasks/#deliverables">Tasks</a> page
<p>
</center>

<br />
