---
title: "Disseminate the Survey"
linktitle: " Disseminate the Survey"
menu:
  tasks:
    parent: Deliverables
    weight: 5
type: docs
weight: 5
editor_options: 
  chunk_output_type: console
---

`r blogdown::shortcode("r-walkthrough-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

<style>
ul {
    margin-left: 1.5em
}
</style>

Download the following to 

<center>
```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "files", "example solicitations and descriptions.zip")

downloadthis::download_file(
  path = loc,
  output_name = "Example Survey Solicitaions and Landing/Gratitude Pages",
  button_label = "&nbsp;&nbsp;&nbsp;<span style='color:#ffffff'>Download</span>",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
</center>

<br>
This task involves a multi-step process. After reviewing the documents provided in the download, please follow the directions below

1. Add a landing and gratitude page

2. Create an initial solicitation and follow-up [email](https://www.qualtrics.com/support/survey-platform/distributions-module/email-distribution/emails-overview/) communications 

3. Administer your survey by the end of the 8th week (if possible) but no later than the end of the 9th week. Submit a screenshot of the contents under the [Distribution](https://www.qualtrics.com/support/survey-platform/distributions-module/distributions-overview/) tab after you have sent the initial solicitation.

*Unless there is a need that has been discussed with me, surveys should stay open at least one week and close within two weeks of distribution*

<center>
<p id="rounded_corners">
All incremental deliverables can be found on the main <a href="/tasks/#deliverables">Tasks</a> page
<p>
</center>
