---
title: "P1: The Research Spiel"
linktitle: "P1: The Research Spiel"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  tasks:
    parent: Deliverables
    weight: 7
type: docs
weight: 3
editor_options: 
  chunk_output_type: console
---

<style>
ul {
    margin-left: 1.5em
}

#center {

text-align: center;

}

.article-container {
  max-width: 960px;
}

iframe {
  width: 1px;
  min-width: 100%;
  border:0;
}

#TableOfContents, .docs-toc-title {
  border-left: 1px solid $sta-primary;
  }

td, th, tr, table {
    border: 0 !important;
    border-spacing:0 !important;
  }
  
hr.divider {
  display: inline-block;
  border: 0;
  width: 15%;
}
</style>

<script>
$(document).ready(function(){
  $('[data-toggle="popover"]').popover();   
});
</script>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
```

### <span style="color:#35d6ed">Submission</span>

<i>In class delivery</i>. Please note that there are no make-ups or late attempts accepted for this deliverable.

### <span style="color:#65ddef">Type</span>

<i>Individual Submission</i>. Each student in the course must present on an individual basis.

### <span style="color:#7ae5f5">Description</span>

In a research setting, an elevator pitch is known as a <i>research spiel</i>. It introduces you as a researcher, your research questions, and the significance of your research. Because a research spiel is short, typically  minutes, it is a great way to introduce and share your research with others at formal networking events, academic conferences, casual conversations, or even during an actual elevator ride.

Ultimately, your research spiel should provide a <i>hook</i> and make your listener want to know more about your research! 

### <span style="color:#97ebf4">Structure</span>

A total of five minutes will be allotted for each presentation with 3 minutes given for the spiel and two for questions. Each individual will be scored on two fronts

1. Four criteria as a <i>presenter</i>
    + Adhering to the 3 minute (+/- 10 seconds) timespan
    + Ability to discuss the review conversationally 
    + Completeness/thoroughness of your presentation
    + Address questions<br><br>
2. Two criteria as an <i>audience member</i>
    + Asking meaningful and thoughtful questions
    + Providing feedback to each participant

#### <span style="color:#97ebf4">Delivering a Research Spiel</span>

<p>It is important to <b><i>focus on your audience </i></b> when delivering a research spiel. For instance, if you're pitching your research project to a general audience, it's a good idea to define or leave out technical or disciplinary terminology. Similarly, be sure to define acronyms and use everyday examples or analogies to help your audience understand key concepts that may be unfamiliar to them.</p>

<p>Remember that in a research spiel, it is important to keep it simple and to the point. State your research topic, report your findings, and convey the significance of your work.</p>

#### <span style="color:#97ebf4">Practice is Key</span>

<p>It's a good idea to write out a draft first and read it out loud a few times to make sure it flows and is of appropriate length. </p>
<p>Most importantly, <b><i> practice </i></b>delivering your research spiel a lot. This will help calm your nerves so you don't freeze up when you're about to share your research with others. To make your research spiel not sound robotic, it's a good idea to memorize key points of your research rather than a full script. </p>
<p>And lastly, be <b><i> enthusiastic. </i></b> Recall what first sparked your interest in your research and be sure to convey that to your audience. </p>

#### <span style="color:#97ebf4">Difference Between a Research Spiel, an Elevator Speech, and an Abstract</span>

<p>Although all three serve to present your research and its significance in a concise manner, research spieles, elevator pitches, and abstracts differ in format and purpose. </p>

```{r, echo=FALSE}
tibble(
  criteria <- c("Delivery",
                "Purpose",
                "Length"
                ),
  
  les <- c("Orally",
           "Introduce your content area, its significance to the field; report dominant and emergine outcomes from the synthesis so your audience will learn more about the area and its connectivity to a broader picture",
          "3 minutes"),
  
  tes <- c("Orally",
           "Introduce yourself as a researcher, your research project, and its significance so your audience will want to learn more about your research",
           "30 seconds to 5 minutes"),
          
    abs <- c("Written",
             "Explain your research project and its significance in order to apply for funding (e.g. assistantships, fellowships, scholarships, etc.), present at conferences, publish in journals, or just for kicks",
             "150-300 words"),
  
  .name_repair = "minimal"
  
) %>%
  kbl(col.names = c("", "Literature <i>or</i> Systematic Review Research Spiel", "Typical Elevator Speech", "Abstract"), 
      "html", 
      escape = FALSE,
      align = 'llll') %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2:4, width = "30em", color = "#ffffff", extra_css = 'vertical-align: middle !important;') %>%
  row_spec(0:3, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent")
```

<small><i><p> <b>Note:</b> In the cases where you've already written an abstract for your research paper, you can use it as a starting basis for your research spiel. You can think of your research spiel as a more condensed version of your abstract. Remember, the main purpose of the research spiel is to engage your listeners so they're interested in learning about the details of your project. </p></i></small>

### <span style="color:#c9f6ff">Extra Help?</span>

#### <span style="color:#c9f6ff">Video Examples</span>

<div class="card" style="background-color: #282A35;">
  <!-- header with navigation tabs -->
  <div class="card-header text-white" style="background-color: #282A35; border-bottom: 0px solid #282A35;">
    <ul class="nav nav-tabs card-header-tabs">
      <li class="nav-item">
        <a class="nav-link active" id="who-tab" data-toggle="tab" href="#who" role="tab" aria-controls="who" aria-selected="true">Who</a>
      </li>
      <li class="nav-item">
        <a class="nav-link" id="what-tab" data-toggle="tab" href="#what" role="tab" aria-controls="what" aria-selected="false">What</a>
      </li>
      <li class="nav-item">
        <a class="nav-link" id="where-tab" data-toggle="tab" href="#where" role="tab" aria-controls="where" aria-selected="false">Where</a>
      </li>
      <li class="nav-item">
        <a class="nav-link" id="why-tab" data-toggle="tab" href="#why" role="tab" aria-controls="why" aria-selected="false">Why</a>
      </li>
    </ul>
  </div>
  <!-- card body with tab content -->
  <div class="card-body">
    <div class="tab-content" id="myTabContent">
    <div class="tab-pane fade show active" id="who" role="tabpanel" aria-labelledby="who-tab">
      <div class="embed-responsive embed-responsive-16by9">
        <iframe class="embed-responsive-item" src="https://www.youtube.com/embed/NBa0cnsRMUQ?start=24&amp;end=29" allowfullscreen=""></iframe>
      </div>
      <p class="card-text">Who - Introduce your name and identities as an academic and researcher.</p>
    </div>
  <div class="tab-pane fade" id="what" role="tabpanel" aria-labelledby="what-tab">
      <div class="embed-responsive embed-responsive-16by9">
        <iframe class="embed-responsive-item" src="https://www.youtube.com/embed/rlPloFiK-e8?start=4&amp;end=10" allowfullscreen=""></iframe>
      </div>
      <p class="card-text">What - Share your research topic and question.</p>
    </div>
  <div class="tab-pane fade" id="where" role="tabpanel" aria-labelledby="where-tab"><div class="embed-responsive embed-responsive-16by9">
        <iframe class="embed-responsive-item" src="https://www.youtube.com/embed/Wl_87TdersA" allowfullscreen=""></iframe>
      </div>
      <p class="card-text">Where - Explain where you are doing your research.</p>
      </div>
    <div class="tab-pane fade" id="why" role="tabpanel" aria-labelledby="why-tab"><div class="embed-responsive embed-responsive-16by9">
        <iframe class="embed-responsive-item" src="https://www.youtube.com/embed/Ek3HUNNiTyU" allowfullscreen=""></iframe>
      </div>
      <p class="card-text">Why - Help people see the importance of your research.</p>
      </div>
      </div>  
  </div>
</div>

#### <span style="color:#c9f6ff">Resources</span>
            
<div class="card" style="background-color: #282A35;">
   <div class="card-header" style="background-color: #282A35; border-bottom: 0px solid #282A35;">
  </div>

<div class="relatedPosts">
  <div class="card-body">

<ul>
      <li><strong><a href="/handouts/elevator-speech.pdf" target='_blank'>Sharing Your Research</a> <small><em> (Sheet)</em></small></strong></li>
      <li><strong><a href="https://www.apa.org/science/about/psa/2014/06/elevator-pitch" target='_blank'>APA student led recommendations on successful elevator pitches</a> <small><em> (Guide)</em></small></strong></li>
      <li><strong><a href="https://graduateschool.nd.edu/assets/76988/elevator_pitch_8_28_2012.pdf" target='_blank'>The Elevator Pitch:
Presenting Your Research in Conversation</a> <small><em> (Presentation)</em></small></strong></li>
</ul>
</div>
      </div>  
  </div>
</div>

<hr class="divider">

<small>Adapted from <a href="https://uclalibrary.github.io/research-tips/deconstructing-the-elevator-speech/" target='_blank'>Deconstructing the Elevator Speech</a> by Mary Tran (UCLA Library)</small>
