---
title: "Aims, Scope and Sequencing"
linktitle: "Week 3: Aims, Scope and Sequencing"
output:
  blogdown::html_page:
    toc: true
menu:
  lesson:
    parent: Lessons
    weight: 3
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #006269;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Respond to Posts
Please create **one response** for the post below on Slack. 

- [`#evaluation-definitions`](https://2021edp617.slack.com/archives/C01L18T7NR2){target="_blank"}

### Note about the responding to posts 
Your responses to postings should follow the same basic criteria outlined in the original post. Remember to use the `Reply in thread` option when replying! If you need a reminder on how to do this, please click [here](/lesson/02-lesson/#responses).

## Evaluation Approaches
Look through the CDC's [Types of Evaluations](/handouts/Types of Evaluation.pdf){target="_blank"} document to get yourself familiarized with various approaches to conducting evaluations. It is important to note that *summative evaluations* are not listed.

## Creating Evaluation Teams
Finalize your evaluation teams that must consist of three to four members. Then talk among yourselves to figure out three possible weekly meetings times/days that you can get together to discuss materials about the course and the eventual evaluation. To begin, I will join you on a biweekly basis to discuss items and to answer any questions you may have. If the team appears to be on track as we progress, I will reduce my participation unless needed.

Please fill out the necessary columns in the csv file addressing

```{r echo=FALSE}

readings <- tibble(
  
  column <- c("First Name", 
             "Last Name",
             "Email Address",
             "Meeting Day/Time 1",
             "Meeting Day/Time 2",
             "Meeting Day/Time 3"
  ),
  
  desc <- c(
    "The first names of each team member on separate lines.",
    "The last names of each team member on separate lines.",
    "Corresponding preferential email address on separate lines.",
    "Your team's first choice for a day/time to meet.",
    "Your team's second choice for a day/time to meet.",
    "Your team's last choice for a day/time to meet."
  ),
  
  .name_repair = "minimal"
  
)

```

<center>
```{r, echo=FALSE}
readings %>%
  kbl(col.names = c("Column Name", "Description"), 
      "html", 
      escape = FALSE,
      align = 'll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "30em")
```
</center>

```{r echo=FALSE,eval=TRUE,message=FALSE}
loc <- here::here("static", "files", "evalTeams.csv")

downloadthis::download_file(
  path = loc,
  output_name = "evalTeams",
  button_label = "Download the Form",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
<br>
Also please name your group. Feel free to be serious or have fun with it!

Pick one person to email me with the filled out `.csv` and the name of your group as the file name.

## Learning About Criteria
We'll be covering three primary concepts in evaluation: *criteria*, *standards* and *indicators*. While all three are extremely important, the trait that can have the greatest impact on the planning of an evaluation is in constructing the proper criteria. With that in mind, please view and listen to the **Criterial and Interpretive Evaluation** slideshow. You can also download a [PDF](/slides/Criterial and Interpretive Evaluation/Criterial and Interpretive Evaluation.pdf){target="_blank"} of the presentation. 

```{r echo = FALSE}
knitr::include_url("/slides/Criterial and Interpretive Evaluation/Criterial-and-Interpretive-Evaluation.html")
```

You can move back and forth using <kbd>←</kbd> and <kbd>→</kbd> and toggle fullscreen by pressing <kbd>F</kbd>. Just press <kbd>O</kbd>^[For **O**verview] at any point in your slideshow and a display of all slides, called tile view, will appear. Click on a slide to go there or press <kbd>O</kbd> to exit tile view.
