---
title: "Sampling and Sampling Distributions"
linktitle: "Week 6: Sampling and Sampling Distributions"
output:
  blogdown::html_page:
    toc: true
menu:
  lesson:
    parent: Lessons
    weight: 2
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

### Data Camp
The fifth [Data Camp](https://www.datacamp.com/){target="_blank"} module is due **two Wednesdays** following the completion of the Week 5 class. The module covers types of data sampling, and experiments. In particular, the sections are:

- Language of data
- Study types and cautionary tales 
- Sampling strategies and experimental design
- Case study

### Book Materials
Download the textbook

- [PowerPoint](/slides/Week 6/SSDS_Ch6.pptx){target="_blank"} and
- [Lecture Notes](/lecture_notes/Week 5/SSDS_Ch6.docx){target="_blank"}.

### Class Notes

- Download the class slides: Remember to click on the presentation itself and then you may

  + Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
  + Press the letter **O** at any point to see see a tile view of the slideshow.
  + Use this [link](/slides/Week 6/Slides-Week-6.html){target="_blank"} to view a larger version of slideshow in a new window.
        
```{r echo = FALSE}
knitr::include_url("/slides/Week 6/Slides-Week-6.html")
```

You can download 

- a [PDF](/slides/Week 6/Slides-Week-6R.pdf){target="_blank"} of the presentation above. 
- an [Outline](/lecture_notes/Week6/ICN_Ch6.pdf){target="_blank"}.

### R Walkthrough: NFL Ticket Prices

1. Download the data sets^[You will have to unzip this file. If you are unfamilair with this process, please check the [Unzipping files](/resource/unzipping/) section under Resources for assistance.] and codebooks needed for this walkthrough. Put them wherever you want BUT please remember where they are.

- [Week 6 Walkthrough Data Set](/slides/Week 6/2014-average-ticket-price.csv){target="_blank"}

2. Click on the presentation itself and then you may

- Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
- Press the letter **O** at any point to see see a tile view of the slideshow.
- Use this [link](/slides/Week 6/Slides-Week-6.html){target="_blank"} to view a larger version of slideshow in a new window.

```{r echo = FALSE}
knitr::include_url("/slides/Week 6/Slides-Week-6R.html")
```

You can download 

- a [PDF](/slides/Week 6/Slides-Week-6R.pdf){target="_blank"} of the presentation above. 
- a [script](/slides/Week 6/Slides-Week-6R.R){target="_blank"} file of just the R chunks used in the presentation.


