---
title: "The Importance of Knowing What's Important"
linktitle: "Week 6: The Importance of Knowing What's Important"
output:
  blogdown::html_page:
    toc: true
menu:
  lesson:
    parent: Lessons
    weight: 6
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #006269;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>
  
```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Meeting
Please make sure to meet with me **prior** to conducting your needs assessment.

## Program Evaluation Standards
Take a look at a list of [standards](https://jcsee.org/program/){target="_blank"} that were created by the Joint Committee on Standards for Educational Evaluation. These will likely be updated soon. 

## Evaluation Reports
If you're interested in seeing some examples of evaluation reports, you can download a few here [here](/handouts/example_reports.zip). 

A fairly comprehensive guide on creating a report was created by the CDC and can be downloaded using this [link](/handouts/cdc-developing-eval-report.pdf){target="_blank"}. 

## Logic Model

You will be required to submit a logic model in the proposal and final report. Read [this](/handouts/introducing-logic-models.pdf) document over to get an idea of what they are and how you can use and construct one. You also have access to a [simple model](/handouts/blank-logic-model.zip) and but feel free to use others like those mentioned on this week's [Example](/example/06-example/#more-logic-models) page.

<!--
## Standards Based Evaluation
Posting soon
To get an idea of how standards can be written including those related to evaluation questions and purposes, please view and listen to the **Standards-Based Evaluation** slideshow. You can also download a [PDF](/slides/Standards-Based Evaluation/Standards_Based_Evaluation.pdf){target="_blank"} of the presentation. 

```{r echo = FALSE}
knitr::include_url("/slides/Standards-Based Evaluation/Standards_Based_Evaluation.html")
```

You can move back and forth using <kbd>←</kbd> and <kbd>→</kbd> and toggle fullscreen by pressing <kbd>F</kbd>. Just press <kbd>O</kbd>^[For **O**verview] at any point in your slideshow and a display of all slides, called tile view, will appear. Click on a slide to go there or press <kbd>O</kbd> to exit tile view. For more options, press <kbd>H</kbd> for help.
-->
