---
title: "Sampling and Sampling Distributions"
linktitle: "Week 7: Sampling and Sampling Distributions"
output:
  blogdown::html_page:
    toc: true
menu:
  lesson:
    parent: Lessons
    weight: 2
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

### Data Camp
The fifth [Data Camp](https://www.datacamp.com/){target="_blank"} module is due. The module covers types of data sampling, and experiments. In particular, the sections are:

- Language of data
- Study types and cautionary tales 
- Sampling strategies and experimental design
- Case study

### Class Notes

- Download the class slides: Remember to click on the presentation itself and then you may

  + Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
  + Press the letter **O** at any point to see see a tile view of the slideshow.
  + Use this [link](/slides/Week 7/Slides-Week-7.html){target="_blank"} to view a larger version of slideshow in a new window.
        
```{r echo = FALSE}
knitr::include_url("/slides/Week 7/Slides-Week-7.html")
```

You can download a [PDF](/slides/Week 7/Slides-Week-7.pdf){target="_blank"} of the presentation above. 

### R Walkthrough: An Incomplete Review of Descriptive Statistics Commands in R

Click on the presentation itself and then you may

- Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
- Press the letter **O** at any point to see see a tile view of the slideshow.
- Use this [link](/slides/Week 7/Slides-Week-7.html){target="_blank"} to view a larger version of slideshow in a new window.

```{r echo = FALSE}
knitr::include_url("/slides/Week 7/Slides-Week-7R.html")
```

You can download a [PDF](/slides/Week 7/Slides-Week-7R.pdf){target="_blank"} of the presentation above. 
