---
title: "Estimations"
linktitle: "Week 9: Estimations"
output:
  blogdown::html_page:
    toc: true
menu:
  lesson:
    parent: Lessons
    weight: 2
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

### In Class Notes

- Download the class slides: Remember to click on the presentation itself and then you may

  + Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
  + Press the letter **O** at any point to see see a tile view of the slideshow.
  + Use this [link](/slides/Week 9/Slides-Week-7.html){target="_blank"} to view a larger version of slideshow in a new window.
        
```{r echo = FALSE}
knitr::include_url("/slides/Week 9/Slides-Week-9.html")
```

You can download 

- a [PDF](/slides/Week 9/Slides-Week-9.pdf){target="_blank"} of the presentation. 

### Textbook Class Notes
Download the textbook

- [Ch 7 PDF](/slides/Week 9/SSDS_Ch7.pdf){target="_blank"}, 
- [Ch 7 Outline](/lecture_notes/Week9/SSDS_Ch7.pdf){target="_blank"},
- [Ch 8 PDF](/slides/Week 9/SSDS_Ch8.pdf){target="_blank"}, and
- [Ch 8 Outline](/lecture_notes/Week9/SSDS_Ch8.pdf){target="_blank"}.

### R Walkthrough: Confidence Intervals

Click on the presentation itself and then you may

- Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
- Press the letter **O** at any point to see see a tile view of the slideshow.
- Use this [link](/slides/Week 9/Slides-Week-9.html){target="_blank"} to view a larger version of slideshow in a new window.


```{r echo = FALSE}
knitr::include_url("/slides/Week 9/Slides-Week-9R.html")
```

You can download 

- a [PDF](/slides/Week 9/Slides-Week-9R.pdf){target="_blank"} of the presentation above. 
- a [script](/slides/Week 9/Slides-Week-9R.R){target="_blank"} file of just the R chunks used in the presentation.
