---
title: "Bivariate Tables"
linktitle: "Week 11: Bivariate Tables"
output:
  blogdown::html_page:
    toc: true
menu:
  lesson:
    parent: Lessons
    weight: 9
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

### In Class Notes

- Download the class slides: Remember to click on the presentation itself and then you may

  + Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
  + Press the letter **O** at any point to see see a tile view of the slideshow.
  + Use this [link](/slides/Week 11/Slides-Week-11.html){target="_blank"} to view a larger version of slideshow in a new window.
        
```{r echo = FALSE}
knitr::include_url("/slides/Week 11/Slides-Week-11.html")
```

You can download 

- a [PDF](/slides/Week 11/Slides-Week-11.pdf){target="_blank"} of the presentation. 

### Textbook Class Notes
Download the textbook

- [Ch 9 PowerPoint](/slides/Week 11/SSDS_Ch9.PPTX){target="_blank"}, 
- [Ch 9 Lecture Notes](/lecture_notes/Week11/SSDS_Ch9.docx){target="_blank"},

### R Walkthrough: Comparing Groups

Click on the presentation itself and then you may

- Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
- Press the letter **O** at any point to see see a tile view of the slideshow.
- Use this [link](/slides/Week 9/Slides-Week-9R.html){target="_blank"} to view a larger version of slideshow in a new window.


```{r echo = FALSE}
knitr::include_url("/slides/Week 11/Slides-Week-11R.html")
```

You can download 

- The [PREDIMED Codebook](/slides/Week 11/predimed_codebook.csv){target="_blank"} used in the slideshow.
- a [PDF](/slides/Week 11/Slides-Week-11R.pdf){target="_blank"} of the presentation above. 
- a [script](/slides/Week 11/Slides-Week-11R.R){target="_blank"} file of just the R chunks used in the presentation.
