---
title: "All Paper West Virginia Clinical and Translational Science Institute (WVCTSI) Tracking and Evaluation Reports"
linktitle: "All Paper Versions"
author: "Abhik Roy"
output:
  blogdown::html_page:
    toc: true
menu:
  reports:
    parent: Paper Reports
    weight: 2
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #733367;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(patchwork)
library(knitr)
library(kableExtra)
library(fontawesome)
library(downloadthis)
```

You may download individual reports using the table or all quarterly reports in a compressed format using the download link below.

```{r eval = TRUE, echo = FALSE}
repy10 <-  as.character(fa("book-open", fill = "#7555bc"))

repy9 <-  as.character(fa("book-open", fill = "#bc559c"))

repy8 <-  as.character(fa("book-open", fill = "#55bc75"))

repy7 <-  as.character(fa("book-open", fill = "#e84061"))

repy6 <-  as.character(fa("book-open", fill = "#5f90b0"))

all <- as.character(fa("book-open", fill = "#ebc95e"))

other <- as.character(fa("book-open", fill = "#7a49a5"))
```

```{r eval = TRUE, echo = FALSE}

reports <- tibble(
  
cycle = c(repy10, repy10, repy10,
          repy9, repy9, repy9, repy9,
          repy8, repy8, repy8, repy8,
          repy7, repy7, repy7, repy7,
          repy6, repy6, repy6),
  
year = c("10", "", "",
         "9", "", "", "",
         "8", "", "", "",
         "7", "", "", "",
         "6", "", ""),

quarter = c("3", "2", "1",
            "4", "3", "2", "1",
            "4", "3", "2", "1",
            "4", "3", "2", "1",
            "4", "3", "2"),

download = c("<a href='/paper_reports/Year 10 Quarter 3 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 10 Quarter 2 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 10 Quarter 1 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 9 Quarter 4 Report.pdf' target='_blank'>Link</a>",
              "<a href='/paper_reports/Year 9 Quarter 3 Report.pdf' target='_blank'>Link</a>",
              "<a href='/paper_reports/Year 9 Quarter 2 Report.pdf' target='_blank'>Link</a>",
              "<a href='/paper_reports/Year 9 Quarter 1 Report.pdf' target='_blank'>Link</a>",
              "<a href='/paper_reports/Year 8 Quarter 4 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 8 Quarter 3 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 8 Quarter 2 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 8 Quarter 1 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 7 Quarter 4 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 7 Quarter 3 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 7 Quarter 2 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 7 Quarter 1 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 6 Quarter 4 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 6 Quarter 3 Report.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/Year 6 Quarter 2 Report.pdf' target='_blank'>Link</a>"
             )
)

zipped <- tibble(
  
cycle = c(all),
  
year = c("6-10"),

quarter = c("All available"),

download = c("<a href='/paper_reports/allPaperReports.zip' target='_blank'>Link</a>")

)

others <- tibble(
  
cycle = c(all,
          all),
  
year = c("2021",
         "2020"),

name = c("Membership and Service Utilization",
         "Awareness Survey"),

download = c("<a href='/paper_reports/Membership and Service Utilization.pdf' target='_blank'>Link</a>",
             "<a href='/paper_reports/2020 WVCTSI Awareness Survey Report NL.pdf' target='_blank'>Link</a>"
             )
)
  
```

### Individual Reports
<center>
```{r message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
reports %>%
  kbl(col.names = c("",
                    "Year",
                    "Quarter",
                    ""), 
      format = "html", 
      escape = FALSE,
      align = 'cccc') %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "10em") %>% 
  row_spec(c(0:16), extra_css = 'vertical-align: middle !important;') 
```
</center>

### All Quarterly Reports
<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
zipped %>%
  kbl(col.names = c("",
                    "",
                    "",
                    ""), 
      "html", 
      escape = FALSE,
      align = 'cccc') %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "10em") %>% 
  row_spec(c(1), extra_css = 'vertical-align: middle !important;') 
```
</center>

### Other Reports
<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
others %>%
  kbl(col.names = c("",
                    "Year",
                    "Name",
                    ""), 
      "html", 
      escape = FALSE,
      align = 'cccc') %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "10em") %>% 
  row_spec(c(1:2), extra_css = 'vertical-align: middle !important;') 
```
</center>
