---
title: "The Social Network"
linktitle: "Week 2: The Social Network"
menu:
  materials:
    parent: Walkthroughs
    weight: 2
type: docs
weight: 1
output:
  blogdown::html_page:
    toc: true
---

```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
library(here)
library(fontawesome)
```

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

## Snippets!
This is the first of many short walkthroughs created to get you familiar with R and the environment we'll be using. In this session we'll cover how to use start engaging with the end all be all package `igraph` which serves as a foundation for most other network analysis packages. 

First please go ahead and down a copy of everything you'll need to follow along with the walkthrough this week

### Materials

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "walkthroughs", "scripts", "EDP693gWeek2Walkthrough.zip"),
  output_name = "Plot a Graph",
  button_label = "Download the Script",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Walkthrough

<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/plotagraph/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no"  frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

