---
title: "Measures of Central Tendency"
linktitle: "Week 3: Measures of Central Tendency Content"
output:
  blogdown::html_page:
    toc: true
menu:
  materials:
    parent: Content
    weight: 2
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<script>
  function resizeIframe(obj) {
    obj.style.height = obj.contentWindow.document.body.scrollHeight + 'px';
  }
</script>

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #761756;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}

table > tbody > tr:hover > td, table > tbody > tr:hover > th {
  background-color: #ffffff;
}
</style>

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
library(here)
library(DT)
library(scales)
library(latex2exp)
library(showtext)
font_add_google("Roboto Condensed", "roboto")
showtext_auto()
```

## Stock Textbook Notes

```{r echo=FALSE}

pptx_location <- "/lecture_notes/Week 3/SSDS_Ch3.pptx"
docx_location <- "/lecture_notes/Week 3/SSDS_Ch3.docx"

powerpoint_link <- function() {
  paste0("<a target='_blank' href=\"", pptx_location, "\">", as.character(fa("file-powerpoint", fill = "#d04423", width = "2em")), "</a>")
}

word_link <- function() {
  paste0("<a target='_blank' href=\"", docx_location, "\">", as.character(fa("file-word", fill = "#00a4ef", width = "2em")), "</a>")
}

textitems <- tibble(
  
  pptx <- c("Chapter 3 PowerPoint",
               powerpoint_link()),
  
  docx <- c("Chapter 3 Notes",
            word_link())
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(textitems, 
      col.names = c("", ""),
      escape = FALSE,
      align = 'cc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1:2, width = "20em", extra_css = 'vertical-align: middle !important;', background = "#ffffff")
```
</center>

## In Class Presentations
For all slideshows, you may move back and forth using <kbd>←</kbd> and <kbd>→</kbd> and toggle fullscreen by pressing <kbd>F</kbd>. Just press <kbd>O</kbd>[^1] at any point in your slideshow and a display of all slides, called tile view, will appear. Click on a slide to go there or press <kbd>O</kbd> to exit tile view. For more options, press <kbd>H</kbd> for help.

### Concepts

<center>
```{r echo = FALSE}
knitr::include_url("/slides/Week 3/Slides-Week-3.html")
```
</center>

```{r echo=FALSE}

html_location <- "/slides/Week 3/Slides-Week-3.html"
pdf_location <- "/slides/Week 3/Slides-Week-3.pdf"

html_link <- function() {
  paste0("<a target='_blank' href=\"", html_location, "\">", as.character(fa("person-chalkboard", fill = "#7ead86", width = "3em")), "</a>")
}

pdf_link <- function() {
  paste0("<a target='_blank' href=\"", pdf_location, "\">", as.character(fa("file-pdf", fill = "#f40f02", width = "2em")), "</a>")
}

slideshowitems <- tibble(
  
  html <- c("Full Screen Slideshow",
               html_link()),
  
  pdf <- c("Presentation PDF",
            pdf_link())
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(slideshowitems, 
      col.names = c("", ""),
      escape = FALSE,
      align = 'cc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1:2, width = "20em", extra_css = 'vertical-align: middle !important;', background = "#ffffff")
```
</center>

### R Walkthrough

<center>
```{r echo = FALSE}
knitr::include_url("/slides/Week 3/Slides-Week-3R.html")
```
</center>

```{r echo=FALSE}

htmlR_location <- "/slides/Week 3/Slides-Week-3R.html"
pdfR_location <- "/slides/Week 3/Slides-Week-3R.pdf"

htmlR_link <- function() {
  paste0("<a target='_blank' href=\"", htmlR_location, "\">", as.character(fa("person-chalkboard", fill = "#7ead86", width = "3em")), "</a>")
}

pdfR_link <- function() {
  paste0("<a target='_blank' href=\"", pdfR_location, "\">", as.character(fa("file-pdf", fill = "#f40f02", width = "2em")), "</a>")
}

slideshowRitems <- tibble(
  
  htmlR <- c("Full Screen Slideshow",
               htmlR_link()),
  
  pdfR <- c("Presentation PDF",
            pdfR_link())
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(slideshowRitems, 
      col.names = c("", ""),
      escape = FALSE,
      align = 'cc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1:2, width = "20em", extra_css = 'vertical-align: middle !important;', background = "#ffffff")
```
</center>

[^1]: For <b>O</b>verview
