---
title: "Evaluation Networks"
linktitle: "Week 3: Evaluation Networks"
menu:
  materials:
    parent: Walkthroughs
    weight: 3
type: docs
weight: 1
output:
  blogdown::html_page:
    toc: true
---

```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
library(here)
library(downloadthis)
```

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

### What is Program Evaluation?

- Directions: Click on the presentation itself and then you may

  + Move back and forth through the slideshow using the ⬅ and ⮕ buttons on your keyboard.
  + Press the letter **O** at any point to see see a tile view of the slideshow.
  + Use this [link](/slides/Intro to PE/Intro-to-PE.html){target="_blank"} to view a larger version of slideshow in a new window.

```{r echo = FALSE}
knitr::include_url("/slides/Intro to PE/Intro-to-PE.html")
```

You can download 

- a [PDF](/slides//Intro to PE/Intro-to-PE.pdf){target="_blank"} of the presentation.

## Snippets!
First please go ahead and down a copy of the script which will which you can use to follow along.

### Script

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "walkthroughs", "scripts", "EDP693gWeek3Walkthrough.zip"),
  output_name = "Load a csv Walkthrough",
  button_label = "Download the Scripts and Files",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Walkthrough

#### Part I: Introduction and Outline of (Some) Utilizable Formats
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/loadacsv/1intro/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no"  frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part II: Graph an Edge List
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/loadacsv/2edgelist/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no"  frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part III: Convert an Edge List to an Adjacency Matrix
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/loadacsv/3convertto/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no"  frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part IV: Graph an Adjacency Matrix
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/loadacsv/4adjacency/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no"  frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part V: Convert an Adjacency Matrix to an Edge List
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/loadacsv/5convertfrom/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no"  frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>
