---
title: "Centralities and Egos"
linktitle: "Week 9: Centralities and Egos"
menu:
  materials:
    parent: Walkthroughs
    weight: 9
type: docs
weight: 1
output:
  blogdown::html_page:
    toc: true
---

```{r load_packages, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
library(here)
library(downloadthis)
```

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}ZD

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}

hr {
    margin: 30px 0;
    height: 1px;
    border: none;
    background: -webkit-gradient(linear, 0 0, 100% 0, from(transparent), to(transparent), color-stop(50%, black));
}
</style>

<!--
## What is Program Evaluation?

First please go ahead and down a copy of everything you'll need to follow along with the walkthrough this week

### Materials

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "walkthroughs", "scripts", "EDP693gWeek3Walkthrough.zip"),
  output_name = "Better Visuals Walkthrough",
  button_label = "Download the Scripts and Files",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

You can move back and forth using <kbd>←</kbd> and <kbd>→</kbd> and toggle fullscreen by pressing <kbd>F</kbd>. Just press <kbd>O</kbd>^[For **O**verview] at any point in your slideshow and a display of all slides, called tile view, will appear. Click on a slide to go there or press <kbd>O</kbd> to exit tile view. For more options, press <kbd>H</kbd> for help.

> Want to see a larger version of the presentation? Click [here](/slides/Intro to PE/Intro-to-PE.html){target="_blank"}.

> Want a PDF you can use offline? Click [here](/slides/Intro to PE/Intro-to-PE.pdf){target="_blank"} of the presentation.
-->

## Snippets!

### Materials

First please go ahead and down a copy of everything you'll need to follow along with the walkthrough this week which covers communities and cliques

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "walkthroughs", "scripts", "EDP693gWeek9Walkthrough.zip"),
  output_name = "Centralities and Egos and Interactives",
  button_label = "Download the Scripts",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Walkthrough

#### Part I: Translation Matrix
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/centrality/centrality1/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no" frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part II: Forever Wrangling
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/centrality/centrality2a_wrangling/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no" frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part III: Building a Graph Framework
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/centrality/centrality2b_building/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no" frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part IV: Tidy Tidy Graphs
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/centrality/centrality2c_tidygraphs/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no" frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

#### Part V: Ego Ego Graphs
<center>
<iframe class="smart-player-embed-container-iframe" id="embeddedSmartPlayerInstance" src="/walkthroughs/videos/centrality/centrality2d_egographs/media/index_player.html?embedIFrameId=embeddedSmartPlayerInstance" width="640" height="360" frameborder="0" scrolling="no" frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>
</center>

<hr>

#### Links
1. Aesthetics
    a. [hex colors](https://www.color-hex.com/){target="_blank"}
    b. [r-color-palettes](https://github.com/EmilHvitfeldt/r-color-palettes){target="_blank"}
    c. [`showtext`](https://cran.rstudio.com/web/packages/showtext/vignettes/introduction.html){target="_blank"}
    d. [`wesanderson`](https://github.com/karthik/wesanderson){target="_blank"}
    
2. Layouts
    a. [ graphlayouts](http://graphlayouts.schochastics.net/){target="_blank"}
    b. [Introduction to ggraph: Layouts](https://www.data-imaginist.com/2017/ggraph-introduction-layouts/){target="_blank"}
  
3. Centrality
    a. [Network analysis of Game of Thrones](https://datascienceplus.com/network-analysis-of-game-of-thrones/){target="_blank"}
  
4. MCU Data
    a. [Which Marvel Characters and Movies are the Most Central?](https://felixluginbuhl.com/blog/posts/2018-01-26-network/){target="_blank"}^[Inspiration for this walkthrough]
   b. [Liste des films de l'univers cinématographique Marvel](https://fr.wikipedia.org/w/index.php?title=Liste_des_films_de_l%27univers_cin%C3%A9matographique_Marvel&oldid=144793972#Personnages){target="_blank"}   
   c. [Marvel Cinematic Universe: Phase One](https://en.wikipedia.org/wiki/Marvel_Cinematic_Universe:_Phase_One){target="_blank"}
   d. [Marvel Cinematic Universe: Phase Two](https://en.wikipedia.org/wiki/Marvel_Cinematic_Universe:_Phase_Two){target="_blank"}
   e. [Marvel Cinematic Universe: Phase Three](https://en.wikipedia.org/wiki/Marvel_Cinematic_Universe:_Phase_Three){target="_blank"}
  
5. [R for Data Science](https://r4ds.had.co.nz/){target="_blank"}
    a. [14: Strings](https://r4ds.had.co.nz/strings.html){target="_blank"}
    b. [16: Dates and times](https://r4ds.had.co.nz/dates-and-times.html){target="_blank"}

6. `vizNetwork`
    a. [*example*](https://www.nagraj.net/notes/visnetwork/){target="_blank"}
    b. [*example*](https://rpubs.com/a_pear_9/visNetwork){target="_blank"}
    c. [`vizNetwork` documentation](https://datastorm-open.github.io/visNetwork/){target="_blank"}
    
7. Wrangling
    a. [Data Imaginist](https://www.data-imaginist.com/2017/introducing-tidygraph/){target="_blank"}
    b. [*example*](http://users.dimi.uniud.it/~massimo.franceschet/ns/syllabus/make/tidygraph/tidygraph.html){target="_blank"}
    c. [*example*](https://rstudio-pubs-static.s3.amazonaws.com/307087_0a7a54f46d5d44b5829c6452484db638.html){target="_blank"}
    
