---
title: ' Plan for Second Half of Class '
subtitle: "EDP 612 Week 8"
author: "Carinna Ferguson"
# date: 2022-03-02
output: 
 xaringan::moon_reader:
   css: ['xaringan-themer.css', 'custom.css']
   nature:
     ratio: 16:9
     highlightStyle: github
     highlightLines: true
     countIncrementalSlides: false
     navigation:
         scroll: false
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.6.0/jquery.min.js"></script>

<script type="text/x-mathjax-config">
MathJax.Hub.Register.StartupHook("TeX Jax Ready",function () {
  MathJax.Hub.Insert(MathJax.InputJax.TeX.Definitions.macros,{
    cancel: ["Extension","cancel"],
    bcancel: ["Extension","cancel"],
    xcancel: ["Extension","cancel"],
    cancelto: ["Extension","cancel"]
  });
});
</script>

<style>
section {
    display: flex;
    display: -webkit-flex;
}


section {
    height: 600px;
    width: 60%;
    margin: auto;
    border-radius: 21px;
    background-color: #212121;
}

section p {
    text-align: center;
    font-size: 30px;
    background-color: #212121;
    border-radius: 21px;
    font-family: Roboto Condensed;
    font-style: bold;
    padding: 12px;
    color: #bff4ee;
    margin: auto;
}

#center {

text-align: center;

}

.center p {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.tab {
    display: inline-block;
    margin-left: 40px;
}

td, th, tr, table {
    border: 0 !important;
    border-spacing:0 !important;
  }
  
img.middle { 
vertical-align: middle; 
}

</style>

```{css echo=FALSE}
.highlight-last-item > ul > li,
.highlight-last-item > ol > li {
  opacity: 0.5;
}
.highlight-last-item > ul > li:last-of-type,
.highlight-last-item > ol > li:last-of-type {
  opacity: 1;
}
```

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
library(here)
library(clt)
library(showtext)
font_add_google("Roboto Condensed", "roboto")
showtext_auto()
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#bff4ee",
  table_row_border_color = "#212121",
  table_row_even_background_color = "#212121",
  footnote_font_size = "0.6em",
  header_font_google = xaringanthemer::google_font("Roboto Condensed", "700"),
  text_font_google   = xaringanthemer::google_font("Roboto Condensed", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", 
                                    "animate_css", 
                                    "tachyons"))

xaringanExtra::use_logo(
  image_url = here::here("static", "img", "course_hex.png"),
  link_url = "https://edp612.asocialdatascientist.com",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
)

```

---

class: highlight-last-item
layout: true

---

#  Designing Qualitative Research Instruments 

--


*Things to consider*

--

Interviews

--

+ 1:1 Interviews v. Focus Group Interviews

--

	+ Your relationship to the researched
	
--

+ Three Suggestions for Conducting Qualitative Interviews (Turner, 2010)

--

+ Preparation prior to the interview

--

	+ Developing effective research questions
	
--

	+ Actual interview of the participants
	
--

+ Developing An Interview Protocol

.footnote[[Three Suggestions for Conducting Qualitative Interviews (Turner, 2010)](https://kodu.ut.ee/~hellex/aya/kirjandus/meetod/ArtikkelIntervjuudest.pdf)]

---

#  Designing Qualitative Research Instruments 

--

Three Suggestions for Conducting Qualitative Interviews

--

+ Preparation prior to the interview

--

	+ Choose a setting with privacy and limited distraction
	
--

	+ Explain the purpose of the interview, the structure, and about how long it will take
	
--

	+ Allow participant to ask questions before you begin
	
--

	+ Have some way to record the interview prepared ( ie video, audio, etc )
	
--

	+ Consider pilot testing your interview protocol!
	
--

+ Developing effective research questions for the interview

--

+ Actual interview of the participants

---

#  Designing Qualitative Research Instruments 

Three Suggestions for Conducting Qualitative Interviews

--

+ Preparation prior to the interview

--

	+ Developing effective research questions for the interview
	
--

		+ Open-ended wording
		
--

		+ Neutral questions (avoid questions that are judgmental or leading)
		
--

		+ Ask questions one at a time – Don’t double barrel questions!
		
--

		+ Clear,  easily understood questions
		
--

		+ Ask follow up and probing questions as appropriate to learn more about participant’s experiences.
		
--

	+ Actual interview of the participants

---

#  Designing Qualitative Research Instruments 

--

Three Suggestions for Conducting Qualitative Interviews

--

+ Preparation prior to the interview

--

  + Developing effective research questions for the interview
	
--

+ Actual interview of the participants
	
--

	+ Double check throughout that your audio recorder is still recording!
		
--

	+ Ask one question at a time
		
--

	+ Try to remain neutral during the interview
		
--

	+ Encourage responses with nodding and/or affirmative words
		
--

	+ Provide transition between questions “I am now going to ask some questions about a different topic” or “Shifting gears to a different question”
		
--

	+ Maintain control of the interview – keep interview on task and relevant to research!

---

#  Developing an Interview Protocol 

--

+ Initial priority is developing a rapport with the participant

--

	+ Communicate the purpose of the research
	
--

	+ Review consent form
	
--

	+ Begin with broad, general, open-ended questions that are easy for the participant to answer
	
--

	+ Ask high-risk questions later in the interview after rapport has been developed
	
--

	+ Ensure the questions you are asking will actually answer your research questions!
	
	
.footnote[Research in the College Context: Approaches and Methods.(2015).United Kingdom:Taylor & Francis]

---

#  Designing a Qualitative Survey 

+ Many of the same points as before!

--

	+ Explain the purpose of the interview, the structure, and about how long it will take
	
--

	+ Open-ended wording
	
--

	+ Neutral questions (avoid questions that are judgmental or leading)
	
--

	+ Ask questions one at a time – Don’t double barrel questions!
	
--

	+ Clear,  easily understood questions
	
--

	+ Consider pilot testing your survey prior to sending it to your participants!
	
--

	+ Ensure the questions you are asking will actually answer your research questions!
	
--

*Next week and the week after we will talk more about making sure surveys meet these requirements!*

---

#  Being and Becoming a Researcher Activity 

---

#  In Your Groups 

--

+ Find a way to record your discussion! I recommend using someone’s phone.

--

	+ Discuss as a group (in an interview-style format) questions on the following slide related to being and becoming a researcher

--

	+ Feel free to deviate from the set questions as appropriate
	
--

	+ Listen to the recording individually and begin to generate some initial codes, or things you feel were important parts of your conversation
	
--

	+ Discuss your initial codes as a group – Come together as a group to generate some broader codes or themes from your conversation
	
--

	+ Be prepared to share your themes and codes with the class
	
--

		+ Provide some quotes to use as examples for any codes you all agreed on or any themes you identified.
		
--

			+ You do not need to display all of your codes!
			
--

		+ You may want to make a 1-2 slide PowerPoint to display your codes and themes.
		
--

.footnote[Note: Record your conversation for about 15 minutes, then begin individual initial coding! Come back to class after ~ 25-30 minutes!]

---

#  Questions to Consider 

---

#  Sharing with the Class 

---

#  Parts of a Qualitative Manuscript? 

--

+ https://www.apa.org/pubs/journals/features/qualitative-manuscript-guidelines.pdf

--

	+ I will put this PDF in the Slack!
	
--

	+ This outlines how to write a qualitative manuscript but is useful for thinking about where to find information in published qualitative research!
	
--

.footnote[[https://www.apa.org/pubs/journals/features/qualitative-manuscript-guidelines.pdf](https://www.apa.org/pubs/journals/features/qualitative-manuscript-guidelines.pdf)]

---

#  Ethics in Qualitative Research 

--

+ Informed consent!

--

+ Researcher/Participant Relationship
	
--

	+ Power, Conflicts of Interest
		
--

+ Researcher’s Subjective interpretation
	
--

	+ Subjectivity Statements
		
--

	+ Protection of Participants
	
--

		+ Anonymity, results/narrative not traceable to participant
		
--

		+ Pseudonyms
		
---

# Questions?

