---
title: 'A "Short" Introduction to Experimental and Quasi-Experimental Designs'
subtitle: "EDP 612 Week 5"
author: "Dr. Abhik Roy"
output: 
 xaringan::moon_reader:
   css: ['xaringan-themer.css', 'custom.css']
   nature:
     ratio: 16:9
     highlightStyle: github
     highlightLines: true
     countIncrementalSlides: false
     navigation:
         scroll: false
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.6.0/jquery.min.js"></script>

<script type="text/x-mathjax-config">
MathJax.Hub.Register.StartupHook("TeX Jax Ready",function () {
  MathJax.Hub.Insert(MathJax.InputJax.TeX.Definitions.macros,{
    cancel: ["Extension","cancel"],
    bcancel: ["Extension","cancel"],
    xcancel: ["Extension","cancel"],
    cancelto: ["Extension","cancel"]
  });
});
</script>

<style>
section {
    display: flex;
    display: -webkit-flex;
}

section p {
    margin: auto;
}

section {
    height: 600px;
    width: 60%;
    margin: auto;
    border-radius: 21px;
    background-color: #212121;
}

section p {
    text-align: center;
    font-size: 30px;
    background-color: #212121;
    border-radius: 21px;
    font-family: Roboto Condensed;
    font-style: bold;
    padding: 12px;
    color: #bff4ee;
}

#center {

text-align: center;

}

.center p {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.tab {
    display: inline-block;
    margin-left: 40px;
}
</style>

```{css echo=FALSE}
.highlight-last-item > ul > li,
.highlight-last-item > ol > li {
  opacity: 0.5;
}
.highlight-last-item > ul > li:last-of-type,
.highlight-last-item > ol > li:last-of-type {
  opacity: 1;
}
```

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(patchwork)
library(knitr)
library(kableExtra)
library(fontawesome)
library(here)
library(DT)
library(scales)
library(latex2exp)
library(rvest)
library(showtext)
font_add_google("Roboto Condensed", "roboto")
showtext_auto()
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#bff4ee",
  table_row_border_color = "#212121",
  table_row_even_background_color = "#212121",
  footnote_font_size = "0.6em",
  header_font_google = xaringanthemer::google_font("Roboto Condensed", "700"),
  text_font_google   = xaringanthemer::google_font("Roboto Condensed", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", 
                                    "animate_css", 
                                    "tachyons"))

xaringanExtra::use_logo(
  image_url = here::here("static", "img", "course_hex.png"),
  link_url = "https://edp612.asocialdatascientist.com",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
)

```

```{r echo = FALSE, eval = TRUE, message=FALSE}
library(tidyverse)
``` 

# A Typical List of Variable Types

--

> There are just so many!

--

<br>
> You may need to memorize these in the future but for now, this is a not very comprehensive list


--

<br>
> Mostly jargon free because communication is more important than sounding smart


--

<br>
> Popular falesly attributed quotes but still apply:

  >-  *You do not really understand something unless you can explain it to your grandmother*
  
  >- *If you can't explain it simply, you don't understand it well enough*
  
  >- *Explain it to me like I'm an idiot*

---

## The Basic Comparisons

.pull-left[ 
<span style="color:#729ec6;">Independent</span>
<br>
the cause
] 

--

<br>
.pull-right[ 
<span style="color:#faa1a1;">Dependent</span>
<br>
the effect
] 

--

<br>
.pull-left[ 
<span style="color:#729ec6;">Explanatory</span>
<br>
what is changed
] 

--

<br>
.pull-right[ 
<span style="color:#faa1a1;">Response</span>
<br>
what happens from that change
] 

--

<br>
.pull-left[ 
<span style="color:#729ec6;">Mediator</span>
<br>
something that can somewhat or fully explain cause and effect
] 

--

<br>
.pull-right[ 
<span style="color:#faa1a1;">Moderator</span>
<br>
something that impacts the direction and/or strength between cause and effect 
] 

---

## The Basic Ones Without Good Comparisons

--

<center>
<span style="color:#b6d7a8;">Extraneous</span>
<br>
<br>
something known but not being studied that could influence cause and effect
</center>

--

<br>
<center>
<span style="color:#b6d7a8;">Confounding</span>
<br>
<br>
something not known that could influence cause and effect
</center>

--

<br>
<center>
<span style="color:#b6d7a8;">Control</span>
<br>
<br>
a baseline that doesn't change
</center>

---

# Part I: Nonexperimental Research

- Lacks the manipulation of an independent variable

--

- While we cannot show causation, this type of research is still very important
		
---

##  When Should We Use Non-Experimental Research? 

--

-  You only have a single variable

--

-  You have a non-causal relationship between variables

--

- There is a causal relationship, but you can’t (practically or ethically) randomly assign participants

--

- There's a broad or exploratory question that needs answered

--

- Need to make sense of data

--

- *Examples*

  > *Does damage to a person’s hippocampus impair the formation of long-term memory traces?*
  
  > *Is there some relationship between verbal intelligence and mathematical intelligence? *
  
  > *How accurate are people’s first impressions?*
  
  > *What is it like to be a working mother diagnosed with depression?*

---

## Types: Correlational Research

---

###  What is Correlational Research? 

- Non-experimental research design used to assess the statistical relationship between two variables

--

- Little to no effort is used to account for confounding variables

---

###  Why Do Correlation Research? 

- If there’s no correlation, then there can’t be eventual causation

--

- Ideas for future experiments

--

- Some studies are too impractical or unethical to be done using an experiment

---

###  Goals for Correlation  

--

1. *Descriptive*. 

--

  - Describes relationships
  
--
  
  - *Example*. “Does bragging about wealth correlate with scores on the [Narcissistic Personality Inventory](https://openpsychometrics.org/tests/NPI/)?”

--

2. *Predictive*. 

--

  - Predict behavior
  
--

  - *Example*. “If a rich person scores 34 (greater level of narcissism) on the Narcissistic Personality Inventory (predictor variable), can we can predict that individual is more likely to brag about wealth (outcome variable)?”

---

###  Maybe / Could Be vs Probably / Certainly

--

.pull-left[ 
<center>
<span style="color:#faa1a1;">Correlational</span>
<hr style="width:50%;">
</center>
]

--

.pull-right[ 
<center>
<span style="color:#729ec6;">Experimental</span>
<hr style="width:50%;">
</center>
]

--

<br>
.pull-left[ 
<center>
<span style="color:#fdd1d1;">Cannot determine cause</span>
</center>
]

--

.pull-right[ 
<center>
<span style="color:#a8c3dc;">Causal</span>
</center>
]

--

<br>
.pull-left[
<center>
<span style="color:#fdd1d1;">Cannot control variables</span>
</center>
]

--

.pull-right[
<center>
<span style="color:#a8c3dc;">Experimental control</span>
</center>
]

--

<br>
.pull-left[
<center>
<span style="color:#fdd1d1;">Observe and describe possible relationships</span>
</center>
]

--

.pull-right[
<center>
<span style="color:#a8c3dc;">Manipulate and describe changes</span>
</center>
]

--

<br>
.pull-left[
<center>
<span style="color:#fdd1d1;">Find individual differences</span>
</center>
]

--

.pull-right[ 
<center>
<span style="color:#a8c3dc;">Find group differences</span>
</center>
]

---

### Sometimes Making Sense Out a Mess

```{r, echo=FALSE,  warning=FALSE, message=FALSE, error=FALSE}
auto <- read_csv("data/Auto.csv",
                 show_col_types = FALSE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, out.width="25%"}
neg <- 
  ggplot(data=auto, mapping = aes(x = weight, y = mpg)) + 
  geom_point(aes(color = origin),
             shape = 21,
             show.legend = FALSE) +
 scale_color_distiller(palette = "Spectral") +
 theme_void(base_family = "roboto") +
 theme(plot.title = element_text(color = "#ffffff",
                                 hjust = 0.5,
                                 size = 20),
       plot.background = element_rect(fill = "#212121",
                                      color = "#212121"),
       panel.border = element_blank()) +
  ggtitle("Negative Correlation")
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, out.width="25%"}
pos <- 
  ggplot(data=auto, mapping = aes(x = weight, y = horsepower)) + 
  geom_point(aes(color = origin),
             shape = 21,
             show.legend = FALSE) +
 scale_color_distiller(palette = "Spectral") +
 theme_void(base_family = "roboto") +
 theme(plot.title = element_text(color = "#ffffff",
                                 hjust = 0.5,
                                 size = 20),
       plot.background = element_rect(fill = "#212121",
                                      color = "#212121"),
       panel.border = element_blank()) +
  ggtitle("Postive Correlation")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, out.width="25%"}
no <-
  ggplot(data=auto, mapping = aes(x = weight, y = acceleration)) + 
  geom_point(aes(color = origin),
             shape = 21,
             show.legend = FALSE) +
 scale_color_distiller(palette = "Spectral") +
 theme_void(base_family = "roboto") +
 theme(plot.title = element_text(color = "#ffffff",
                                 hjust = 0.5,
                                 size = 20),
       plot.background = element_rect(fill = "#212121",
                                      color = "#212121"),
       panel.border = element_blank()) +
  ggtitle("Weak or No Correlation")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.height=5, fig.width=15, fig.align='center'}
neg + no + pos + 
  plot_annotation(
    theme = theme(plot.background = element_rect(fill = "#212121",
                                                 color = "#212121"))
  )
```

---

# Calendar of Tasks

```{r echo=FALSE}
taskitems <- tibble(
  
  task = c("L0",
           "L1",
           "L2",
           "L3",
           "L4",
           "L5",
           "L6"),
  
  description = c("L0: Lit Review Process",
           "L1: Topic Selection & Annotated Bib",
           "L2: Annotated Bibliography",
           "L3: Lit Review First Draft",
           "L4:  Lit Review Second Draft",
           "L5: Lit Review Third Draft",
           "L6: Lit Review Final Version!"),
  
  due = c("Week 3",
          "Week 5",
          "Week 7",
          "Week 9",
          "Week 11",
          "Week 13",
          "Week 15 <sup>1</sup>")
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(taskitems, 
      col.names = c("", "", ""),
      escape = FALSE,
      align = 'cll') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "5em", color = "#ffffff", extra_css = 'vertical-align: middle !important;') %>%
  column_spec(2, width = "20em", color = "#ffffff", extra_css = 'vertical-align: middle !important;') %>%
  column_spec(3, width = "10em", color = "#ffffff", extra_css = 'vertical-align: middle !important;') 
```
</center>

<a style="font-size:14px;"><sup>1</sup>This is the week of final exams.</a>

---

# Part II: Experimental Design 

---

#  Two Features of an Experiment 

--

+ Manipulation of the Independent Variable

--

	+ Can “cause” this independent variable to occur
	
--

	+ This “cause” elicits the response (depenedent variable)
	
--

	+ Random Sampling
	
--

	+ Control of Extraneous Variables
	
--

	+ Can hold variable(s) constant
	
--

	+ Limit variable to a specific category
	
--

	+ (Random Assignment)
	
--

*Quasi Experiment* - Can typically manipulate the IV, but cannot randomly assign participants to conditions

---

#  Types of Treatment & Control Groups  

--

+ Randomized clinical trial

--

	+ One group gets the “treatment” and another group doesn’t –the control
	
--

	+ No-treatment control condition	
--

	+ Zero Treatment (they get nothing)	
--

	+ Problem: placebo effect	
--

	+ Placebo Control group	
--

	+ Given Placebo	
--

	+ Checks for placebo effect	
--

	+ Wait-list control condition	
--

	+ Delayed treatment	
--

	+ Checks for “expectation of improving”

---

## Random vs. Random
 
--

.pull-left[ 
<center>
<span style="color:#faa1a1;">Random Sampling</span>
<hr style="width:50%;">
</center>
]

--

.pull-right[ 
<center>
<span style="color:#729ec6;">Random Assignment</span>
<hr style="width:50%;">
</center>
]

--

<br>
.pull-left[ 
<center>
<span style="color:#fdd1d1;">Cannot determine cause</span>
</center>
]

--

.pull-right[ 
<center>
<span style="color:#a8c3dc;">Causal</span>
</center>
]

--

<br>
.pull-left[
<center>
<span style="color:#fdd1d1;">Cannot control variables</span>
</center>
]

--

.pull-right[
<center>
<span style="color:#a8c3dc;">Experimental control</span>
</center>
]

--

<br>
.pull-left[
<center>
<span style="color:#fdd1d1;">Observe and describe possible relationships</span>
</center>
]

--

.pull-right[
<center>
<span style="color:#a8c3dc;">Manipulate and describe changes</span>
</center>
]

--

<br>
.pull-left[
<center>
<span style="color:#fdd1d1;">Find individual differences</span>
</center>
]

--

.pull-right[ 
<center>
<span style="color:#a8c3dc;">Find group differences</span>
</center>
]
 

---

#  Types of Designs 

--

+ Between Subjects Experiments

--

	+ Each participant tested only once
	
--

	+ Relies on random assignment	
--

	+ Matched group design	

--

+ Simultaneous Within Subject Design	

--

	+ Mixed trials/conditions
	
---

+ Within subject Experiments
	
--

	+ Each participant tested in all conditions (Blocked)	
	
--

	  + Order Effects	

--

	  + Carryover Effects
		
--

		+ Practice Effects
		
--

		+ Fatigue effect
		
--

		+ Context effects
		
--

	+ Counterbalancing

--

	   + Repeated

---

#  Which One is Better? 

--


Between Subject

--

+ Conceptually simple

--

	+ Less testing time for an individual
	
--

	+ Avoids carryover effects and no need for counterbalancing
	
--

	+ *Best when you only get one shot

--

Within Subject

--

+ Controls for extraneous participant variables (lowered noise)

--

	+ Fewer subjects
	
--

	+ Less testing time overall
	
--

	+ *Best option if the participant has time and don’t think carryover is an issue
	

---

# Design an experiment

1. Go to [Open Psychometrics](https://openpsychometrics.org)

2. Take one of the assessments with your partner

3. Design an experimental study 
  
  - What are you testing?
  
  - Who are you testing?
  
  - What are you testing for?
  
  - What are you measuring?
  
  - What do you expect to happen?
  
--
  
Be prepared to talk about them in about 30 minutes.

---

#  That’s it! 

Any questions?
