---
title: "The In-Crowd"
linktitle: "Week 5: The In-Crowd"
menu:
  tasks:
    parent: Homeworks
    weight: 5
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## R Task

First please go ahead and down a copy of everything you'll need to complete this week's task

### Materials

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "data", "EDP693gWeek5Task.zip"),
  output_name = "flightsandchords",
  button_label = "Download the Data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Directions

1. Load up the `flights.csv` file which is a collection of the airports with the most traffic and smaller airports (given by Other) in the United States. Create a chord diagram such that the following criteria are met:<br><br>
    a. Cities are colored differently by their time zone. (Eastern Time, Central Time, Mountain Time, Pacific Time, Alaskan Time, Hawaiian Time). However, color choices are left up to you<br><br>
    b. The thickness of links between cities implies the relative frequency of flights between two cities (i.e. the thicker links represent more frequent flights).<br><br>
    c. The links are directed, in that when the color of a link matches the outer band, it is a point of origin (departure). Consequentially this implies that when the color of a link does not match the outer band, it is a point of destination (arrival).<br><br>
    d. There is a legend with the colors and corresponding time zones clearly marked.<br><br>
    e. Make adjustments to the map to make it visually appealing (do.

2. Please post both

- a copy of your script as a `.R` or `.Rmd` file
- the output as a `pdf` or `png` file to

[#r-flights](https://2021edp693g.slack.com/archives/C02FLL86H4M){target='_blank'} no later than October 6 at 11:59 PM.
