---
title: "Finding Feelings"
linktitle: "Week 7: Finding Feelings"
menu:
  tasks:
    parent: Homeworks
    weight: 7
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## R Task

First please go ahead and down a copy of everything you'll need to complete this week's task

### Materials

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "data", "EDP693gWeek7Task.zip"),
  output_name = "flightsandchords",
  button_label = "Download the Data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Directions

1. There are multiple data sets this week, each consisting of twitter data collected in 2015. Pick one of the data sets that hopefully interests you and conduct a sentiment analysis and network plot of the connected terms. 

2. Please post both

- a copy of your script as a `.R` or `.Rmd` file
- both outputs as  `pdf` or `png` files to

[#r-sentiments](https://2021edp693g.slack.com/archives/r-sentiments){target='_blank'} no later than October 20 at 11:59 PM.
