---
title: "Whose Side Are You on?"
linktitle: "Week 9: Whose Side Are You on?"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  tasks:
    parent: Tasks
    weight: 9
type: docs
weight: 1
---

`r blogdown::shortcode("aes-header")`

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
source(here::here("content", "com_libs.R"))
```

## Writing

### Posting

Evaluations administered within the context of a class are almost never *participatory* simply due to a lack of time and given a semi-controlled environment. However in practice, at least half require or mandate some level of participation within the evaluative process. 

Given that, the level of stakeholder/sponsor involvement in the planning, execution, and reporting of a study may have an effect on its efficacy and utility. Take a bit to think about the following three items and when you're ready, address them in a single post on the channel [#wk9-participatory-evaluations](https://edp617spring2023.slack.com/archives/C04SEH1CQBW).

Take a look at the figure below and address the items below
    + assess the level of stakeholder/sponsor participation you are comfortable with (horizontal axis)
    + assess the effect on evaluation outcomes based on your choice (vertical axis)
    + choose a label that best represents your position 
  
```{r echo=FALSE, message=FALSE, warning=FALSE, out.extra = 'style="display: block;margin-left: auto;margin-right: auto;width: 90%;"'}
# constants
axis_begin <- -2
axis_end <- 2
total_ticks <- 10

# DATA ----
# point to plot
my_point <- 
  data.frame(x = 1, 
 y = 1)

# chart junk data
tick_frame <- 
  data.frame(ticks = seq(axis_begin, 
 axis_end, 
 length.out = total_ticks), 
 zero = 0) %>%
  subset(ticks != 0)

lab_frame <- 
  data.frame(lab = seq(axis_begin, 
   axis_end),
 zero = 0) %>%
  subset(lab != 0)

tick_sz <- (tail(lab_frame$lab, 1) - lab_frame$lab[1]) / 128

# PLOT ----
ggplot(my_point, aes(x,y)) +

  # CHART JUNK
  # y axis line
  geom_segment(x = 0, 
   xend = 0, 
   y = lab_frame$lab[1], 
   yend = tail(lab_frame$lab, 1),
   size = 0.5) +
  # x axis line
  geom_segment(y = 0, 
   yend = 0, 
   x = lab_frame$lab[1], 
   xend = tail(lab_frame$lab, 1),
   size = 0.5) +
  # x ticks
  geom_segment(data = tick_frame, 
   aes(x = ticks, 
   xend = ticks, 
   y = zero, 
   yend = zero + tick_sz)) +
  # y ticks
  geom_segment(data = tick_frame, 
   aes(x = zero, 
   xend = zero + tick_sz, 
   y = ticks, 
   yend = ticks)) +
  theme_minimal() + 
  annotate("rect", xmin = -2, xmax = 0, ymin = -2, ymax = 0, fill = "#212121") + 
  annotate("rect", xmin = 0, xmax = 2, ymin = 0, ymax = 2 , fill = "#212121") +
  annotate("rect", xmin = 0, xmax = 2, ymin = -2, ymax = 0, fill = "#212121") + 
  annotate("rect", xmin = -2, xmax = 0, ymin = 0, ymax = 2, fill = "#212121") +
  annotate("label", x = 1, y = 1, label = "A", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = -1, y = 1, label = "B", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = -1, y = -1, label = "C", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = 1, y = -1, label = "D", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  theme(panel.border = element_rect(color = "#d3d3d3", 
fill = "transparent", 
size = 4),
panel.background = element_rect(fill = "#212121"),
plot.background = element_rect(fill = "#212121", 
   color = NA),
panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), 
axis.text.x = element_text(hjust = 0.5,
   vjust = 0.5,
   color = "#a9a9a9",
   size = 10,
   face = "bold",
   margin = margin(t = 5)),
axis.text.y = element_text(hjust = 0.5, 
   vjust = 0.5, 
   angle = 90, 
   color = "#a9a9a9",
   size = 10,
   face = "bold",
   margin = margin(r = 10)),
   axis.title = element_blank())+ 
  geom_hline(yintercept = 0, 
 color = "#d3d3d3", 
 size = 2) + 
  geom_vline(xintercept = 0, 
 color = "#d3d3d3", 
 size = 2) + 
  annotate("label", x = 0, y = 0, label = "O", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = 0, y = 1, label = "AB", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = -1, y = 0, label = "BC", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = 0, y = -1, label = "CD", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  annotate("label", x = 1, y = 0, label = "DA", fontface = "bold", size = 6, color = "#ffffff",
           fill = "#212121") +
  scale_x_continuous(expand = c(0, 0),
 breaks = c(-1.8,-1,0,1,1.8),
 labels = c("Nonparticipatory\nEvaluation", 
            "", 
            "Participatory\nEvaluation", 
            "",
            "Empowerment\nEvaluation")) + 
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(-1.7,-0.9,0,0.9,1.7),
                     labels = c("Negative\neffect on\nFindings",
                                "",
                                "No\neffect on\nFindings",
                                "",
                                "Positive\neffect on\nFindings")) +
  theme(plot.margin = margin(10, 100, 10, 10))
```

1. Interpret and discuss the reason for your selection.

2. Which stages of the evaluation process would you allow and disallow stakeholder/sponsor involvement, if any? Please defend your position.

3. Does stakeholder/sponsor involvement in an evaluation affect the integrity of an evaluation? If so, when would this first start to occur? If not, explain why. Please defend your position.

## Doing 

### Evaluation Checklists

If you are a checklist type of person, consider taking a look at the many examples at the [*Evaluation Checklist Project*](https://wmich.edu/evaluation/checklists) within the The Evaluation Center at Western Michigan University. You can read more about the [validation process](https://wmich.edu/evaluation/checklists/checklistsvalidation) and how to [submit](https://wmich.edu/evaluation/checklists/checklist-submit) one that the project does not have. 

### Deliverables

For a preview of the remaining deliverables, please head over one of the pages listed below

1. [Final Report](/deliverables/04-final-report/)

2. [Presentation of Results](/deliverables/05-presentation-of-results/)
