---
title: "Centralities and Egos"
linktitle: "Week 9: Centralities and Egos"
menu:
  tasks:
    parent: Homeworks
    weight: 9
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## R Task

First please go ahead and down a copy of everything you'll need to complete this week's task

### Materials

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "data", "EDP693gWeek7Task.zip"),
  output_name = "flightsandchords",
  button_label = "Download the Data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

### Directions

1. Locate a table on any website that (a) includes relational data and (b) you have to scrape using `rvest`^[Wikipedia may be an obvious choice given the walkthrough, but you are free to go after any tabular tabular data]

2. Construct 
a. three plots of the data using any three centrality measures and patch them together. Make sure that you interpret what the plot is telling you and that you can justify the comparisons.

b. two plots as ego networks and patch them together Make sure that you interpret what the plot is telling you and that you can justify the comparison.

c. convert one pick into a `Viznetwork`^[have some fun with this!]

3. Please post

- the three comparative plots as a single `pdf` or `png` file 
- the two ego networks as a single `pdf` or `png` file 
- the `Viznetwork` as a working '.html' file
- a copy of your script as a `.R` or `.Rmd` file
- a brief paragraph describing the comparisons any any conclusions that were drawn

in a **single thread**

[#r-sentiments](https://2021edp693g.slack.com/archives/r-centrality_egos){target='_blank'} no later than November 14 at 11:59 PM.
