---
title: "Comparing Groups"
linktitle: "Week 10: Building and Visualizing Bivariate Tables"
author: "Week 10"
output: 
 xaringan::moon_reader:
   css: xaringan-themer.css
   nature:
     ratio: 16:9
     highlightStyle: github
     highlightLines: true
     countIncrementalSlides: false
     navigation:
         scroll: false
---

```{r echo=FALSE}
textcolor <- 
  function(text, color){
  sprintf("<span style='color: %s;'>%s</span>", color, text)
    }
```

<script>
  function resizeIframe(obj) {
    obj.style.height = obj.contentWindow.document.body.scrollHeight + 'px';
  }
</script>

<style>
section {
    display: flex;
    display: -webkit-flex;
}

section p {
    margin: auto;
}

.hljs-github .hljs {
    background: transparent;
    color: #b2dfdb;
}

.hljs-github .hljs-keyword {
    color: #64b5f6;
}

.hljs-github .hljs-literal {
    color: #64b5f6;
}

.hljs-github .hljs-number {
    color: #64b5f6;
}

.hljs-github .hljs-string {
    color: #b7b3ef;
}

section {
    height: 600px;
    width: 60%;
    margin: auto;
    border-radius: 20px;
    background-color: #212121;
}

section p {
    text-align: center;
    font-size: 30px;
    background-color: #212121;
    border-radius: 20px;
    font-family: Roboto Condensed;
    font-style: bold;
    padding: 15px;
    color: #bff4ee;
}

#center {
text-align: center;
}

.center p {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.custom-inline {
  color: #bff4ee;
}

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
library(patchwork)
library(here)
library(compareGroups)
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#bff4ee",
  code_inline_background_color = "transparent",
  code_inline_color = "#b2dfdb",
  code_highlight_color = "#db6464",
  table_row_border_color = "#212121",
  table_row_even_background_color = "#212121",
  footnote_font_size = "0.6em",
  header_font_google = xaringanthemer::google_font("Roboto Condensed", "700"),
  text_font_google = xaringanthemer::google_font("Roboto Condensed", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))

xaringanExtra::use_logo(
  image_url = here::here("static", "img", "course_hex_alpha.png"),
  link_url = "https://edp613.asocialdatascientist.com",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
  )
```

# Packages needed and a Note about Icons

Please load up the following packages. Remember to first install the ones you don't have.
```{r echo = FALSE, eval = TRUE, message=FALSE}
library(tidyverse)
library(compareGroups)
``` 

```{r echo = FALSE, eval = TRUE, message=FALSE}
suppressMessages(library(tidyverse))
suppressMessages(library(compareGroups))
``` 
<br>
<br>
You may come across the following icons. The table below lists what each means.
```{r eval = TRUE, echo = FALSE, purl=FALSE}
forward <- as.character(fontawesome::fa("forward", fill = "
#4682b4"))

stop <- as.character(fontawesome::fa("stop", fill = "#ff6347"))

link <- as.character(fontawesome::fa("link", fill = "#5cb85c"))

bookmark <- as.character(fontawesome::fa("bookmark", fill = "#5cb85c"))


icon_desc <- tibble(
  
  Icon = c(forward,
           stop, 
           link,
           bookmark),
  
  Description = c("Indicates that an example continues on the following slide.",
                  "Indicates that a section using common syntax has ended.",
                  "Indicates that there is an active hyperlink on the slide.",
                  "Indicates that a section covering a concept has ended.")
  
)
```

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, purl=FALSE}
kable(icon_desc, 
      escape = FALSE,
      align = 'cl') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "40em") %>%
  row_spec(0, background = "#181818") %>%
  row_spec(1, background = "#181818") %>%
  row_spec(2, background = "#181818") %>%
  row_spec(3, background = "#181818") %>%
  row_spec(4, background = "#181818") 
```

---

# The `compareGroups` package

- Originally designed to read, interpret, summarize, display and analyze epidemiological data. 

--

- Allows you to create everything from data summaries for quality control.

---

# Starting up

Let's use one of the preloaded data sets: `PREDIMED`.

--

>- longitudinal study containing several baseline characteristics of the participants as well as events occurred during the 7 years follow-up period given by variables `event` and `toevent`.

--

>- Each individual has been assigned to a three intervention diet randomly given by the variable `group`.

--

>- You can read the study via [PubMed](https://pubmed.ncbi.nlm.nih.gov/29897866/)

--

Run the following
```{r eval = TRUE, echo = TRUE}
data("predimed")
```

---

# View the Data

We can take a look at the data by 
```{r eval = TRUE, echo = TRUE}
predimed %>%
  head()
```

---

# Variable Names

You can take a look at the variables in the data set by running
```{r eval = TRUE, echo = TRUE}
names(predimed)
```

--

Well that's not overtly helpful. Oh wait there's a codebook!

```{r echo = FALSE, eval = TRUE}
predimed_vars <- 
  read_csv(here::here("static", "slides", "Week 10", "predimed_codebook.csv"),
           show_col_types = FALSE)
```

```{r echo = TRUE, eval = FALSE}
predimed_vars <- 
  read_csv("predimed_codebook.csv")
```

---

# Code Book 

Ok so let's take a look!

```{r echo = TRUE, eval = TRUE}
predimed_vars
```

---

# Descriptive Tables for Observations

If you want to create a quick table full of descriptives that *aren't meant for exporting*, use the `descrTable()` command

```{r echo = TRUE, eval = TRUE}
descrTable(group ~ ., predimed)
```

---

# Descriptive Tables for Analysis 

If you want to create a table full of descriptives that *you can use for analysis*, use the `compareGroups()` command

```{r echo = TRUE, eval = TRUE}
comparison <- 
  compareGroups(group ~ ., predimed); comparison
```

---

# Subsetting

The previous example gave us the gambit. In `compareGroups(group ~ ., predimed)`, all of the variables were compared to each other. What if we just want to look at a few variables?

In this first example, we'll look at the impact of age, smoking, waist size, and hypercholesterol together on the group

```{r echo = TRUE, eval = TRUE}
compareGroups(group ~ age + smoke + waist + hyperchol, 
              data = predimed)
```

Notice by using the *p*-value from the column `p.value`, we have our first indicator that something happened. It is NOT a guarantee!

---

# A Quick Note About the *p*-value

You may have read articles where the outcomes of a study are labeled as a fact because the results were *statistically significant*. 

--

- **Why isn't this right?** Historically and even to this day, *p*-values are commonly used to test and dismiss $H_0$, which generally states that there is no 

--

  - difference between two groups, or 
  
--

  - correlation between a pair of characteristics.
<br>
<br>

--

<hr>

--

<br>
  Traditionally, the mistake has been in the interpretation and reliance on the notion that 
  
 *the smaller the **p-value**, the less likely an observed set of values would occur by chance.*
  
  So $p\leq0.05$ is generally taken to mean that a finding is statistically significant and therefore warrants publication which the [American Statistical Association](https://www.amstat.org/asa/files/pdfs/p-valuestatement.pdf) and [anyone who knows better than to rely on a single measure](https://www.nature.com/news/how-scientists-fool-themselves-and-how-they-can-stop-1.18517) can tell you is nonsense (what is called dumpster or garbage stats). 

---

# Ok That Wasn't a Quick A Note About the *p*-value

At best the *p*-value is what we call an *indicator* of something happening. Essentially it is one piece of evidence of many!

--

- **What it doesn't mean?** Firstly $p\leq0.05$
***does not imply that there is a 95% chance that $H_0$ is correct.***

- **What it does mean!** It signifies that if the $H_0$ is true and all other assumptions made are valid, then there is a 5% chance of obtaining a result at least as extreme as the one observed. 

  - **Most important?** A *p*-value cannot indicate the importance of a finding
    - *Example*: a medication can have a statistically significant effect on patients’ blood glucose levels without having a therapeutic effect.

--

- **Time to get rid of it?** Well no. It is an indicator but just because its not the end all be all measure doesn't mean it's not useful. So use it *but* also use others with it!
  - *Examples*: There are many but confidence intervals are another piece of information to use. Other approaches include Bayesian methods and effect sizes.

---

# The actual last slide strictly about *p*-values

Here is a good summary...well a summary at least:

--

<br>*p*-values do NOT
  - indicate *reproducibility* or *evidence*
  - *prove* or *disprove* a hypothesis
  - tell you to *accept a hypotheses*

--

<br>*p*-values do
  - indicate that *something is happening*
  - imply a *probability exists*
  - get misinterpreted a lot (and I mean a lot!) yielding *Type I* and *Type II Errors*
  
---

# Back to Subsetting

Now that we hopefully have an idea what the *p*-value implies, let's look at the impact of age, smoking, waist size, and hypercholesterol together on the the sample of females

```{r echo = TRUE, eval = TRUE}
compareGroups(group ~ age + smoke + waist + hyperchol, 
              data = predimed, 
              subset = sex == "Female")
```

--

It seems that `Age` and `Waist circumference` may impact the `Female` population in the study (i.e. sample). We'd have to investigate *all* of the variables more to know for sure.

---

# Getting all of the *p*-values

If we wanted to get an idea if the variables impact each other, we can use

```{r echo = TRUE, eval = TRUE}
pvals <- getResults(comparison, 
                    "p.overall"); pvals
```

--

Remember this is considering all of the variables, not those we subsetted!

---

# APA Tables ...

We can also create an APA 7th edition formatted table!

```{r echo = TRUE, eval = TRUE}
export_comparison <- 
  createTable(comparison); export_comparison
```
--

*Remember this is considering all of the variables, not those we looked at*

---

# ... and Plot ...

And we can also create an APA 7th edition formatted plot!

```{r echo = TRUE, eval = TRUE, out.width = '30%', fig.align='center'}
plot(export_comparison["sex"]) # barplot by sex
```

---

# ... and Other Plots

```{r echo = TRUE, eval = TRUE, warning = FALSE, out.width = '40%', fig.align='center'}
plot(export_comparison["age"]) # histogram and normality plot by age
```


---

# Exporting

Finally you can export your items! Here are some common ways to export tables

```{r echo = TRUE, eval = FALSE}
export2csv(export_comparison, 
           file = "comparison.csv") # as a csv file

export2word(export_comparison, 
            file = "comparison.docx") # as a word file

export2xls(export_comparison, 
           file = "comparison.xls") # as a word file

export2pdf(export_comparison, 
           file = "comparison.pdf") # as a pdf file
```

---

# One More Thing: The GUI

If you do not like the command line interface of R or in general, there is an experimental click-click based built in app you can by typing 

```{r echo = TRUE, eval = FALSE}
cGroupsGUI(predimed)
```

It appears to work fine on a PC. However if you have a Mac and *did not* install [XQuartz](https://www.xquartz.org/) as originally instructed, there is a *statistically significant* chance it may (a) not load or (b) have quirks if it does.

---

## Thats it!
