---
title: "Base R is a Thing"
linktitle: "Week 2: Base R is a Thing"
output:
  blogdown::html_page:
    toc: true
menu:
  assignment:
    parent: Weekly Tasks
    weight: 3
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #733367;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(downloadthis)
library(here)
```
  
### Create Plots in Base R
Use the file `AlcoholConsumption.csv` to create three plots such that two are misleading or misrepresent the data while the other is indicative of what the data truly is. You are asked to stick to Base R even if you have working knowledge of `tidyverse` commands, though this is not a requirement. Please submit this as a single R script replacing only the areas that ask you to do so. 

```{r, eval= FALSE}
# Replace this with your name 

# Misleading/misrepresented 1 ----
## Put your entire code for the plot under this line ----

# ~ Replace this with a basic explanation of why it is misleading and/or misrepresented ----

# --

# Misleading/misrepresented 2 ----
## ## Put your entire code for the plot under this line ----

# ~ A basic explanation of why it is misleading and/or misrepresented ----

# --

# True version ----
## ## Put your entire code for the plot under this line ----

# ~ A basic explanation of why it is misleading and/or misrepresented ----

```

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "exscripts", "week2outline.R"),
  output_name = "Week 2 Script Outline",
  button_label = "Download the Script",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "data", "AlcoholConsumption.csv"),
  output_name = "AlcoholConsumption",
  button_label = "Download the Data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```
<br>
Notice that there are four dashes (`----`) after the text in every `#` except on the line where you should place your name. This provides a nested outline of your script that is easier to follow, especially if they get long. 

There are a few ways to get to your outline. As you transition from a dependence on your mouse/trackpad to the *old school* keyboard, having a working knowledge of shortcuts creates a less disruptive experience than say having to grab that mouse/trackpad everytime you want to do something other than typing. To access the outline of your sections and subsections within an R script, hold down the keys <kbd>control</kbd> <kbd>shift</kbd> <kbd>o</kbd>^[The letter *o* not zero.]

To learn more about nesting, take a look at this post titled [The Little Things]("https://blog.rstudio.com/2020/12/02/rstudio-v1-4-preview-little-things/"){target="_blank"}.

Please submit your script to [eCampus](https://ecampus.wvu.edu/){target="_blank"} under **Week 2 Out of Class Task**.

