---
title: "ggplotting"
linktitle: "Week 3: ggplotting"
output:
  blogdown::html_page:
    toc: true
menu:
  assignment:
    parent: Weekly Tasks
    weight: 3
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #733367;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}
</style>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(downloadthis)
library(here)
```
  
### Create Plots in ggplot

Use the file `Middle-Class-US-Metro-Areas-5-12-16-Supplementary-Tables.xslx` from [Pew Research on America’s shrinking middle class](https://www.pewsocialtrends.org/2016/05/11/americas-shrinking-middle-class-a-close-look-at-changes-within-metropolitan-areas/){target="_blank"} to create at least 5 comparisons based on at the data set. 

Please post a single script to  [`##wk3-shrinking-middle-class`](https://2021edp693e.slack.com/archives/C01MB8CN6D9){target="_blank"}

*NOTE: You will have to clean up the data but do not have to do it in R.*

```{r echo=FALSE,eval=TRUE}
downloadthis::download_file(
  path = here::here("static", "data", "Middle-Class-US-Metro-Areas-5-12-16-Supplementary-Tables.xlsx"),
  output_name = "Middle-Class-US-Metro-Areas-5-12-16-Supplementary-Tables",
  button_label = "Download the Data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  class = "hvr-sweep-to-left"
  )
```


