---
title: "A Map to the Past"
linktitle: "Week 7: A Map to the Past"
output:
  blogdown::html_page:
    toc: true
menu:
  assignment:
    parent: Weekly Tasks
    weight: 7
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

<style>
.hvr-sweep-to-left {
  display: inline-block;
  vertical-align: middle;
  -webkit-transform: perspective(1px) translateZ(0);
  transform: perspective(1px) translateZ(0);
  box-shadow: 0 0 1px rgba(0, 0, 0, 0);
  position: relative;
  -webkit-transition-property: color;
  transition-property: color;
  -webkit-transition-duration: 0.25s;
  transition-duration: 0.25s;
}

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background:	#003277;
  -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}

* {
  box-sizing: border-box;
}

.tabs {
  display: flex;
  flex-wrap: wrap;
  max-width: 700px;
  background: #efefef;
  box-shadow: 0 48px 80px -32px rgba(0,0,0,0.3);
}

.input {
  position: absolute;
  opacity: 0;
}

.label {
  width: 100%;
  padding: 20px 30px;
  background: #e5e5e5;
  cursor: pointer;
  font-weight: bold;
  font-size: 18px;
  color: #7f7f7f;
  transition: background 0.1s, color 0.1s;
}

.label:hover {
  background: #d8d8d8;
}

.label:active {
  background: #ccc;
}

.input:focus + .label {
  box-shadow: inset 0px 0px 0px 3px #2aa1c0;
  z-index: 1;
}

.input:checked + .label {
  background: #fff;
  color: #000;
}

@media (min-width: 600px) {
  .label {
    width: auto;
  }
}

.panel {
  display: none;
  padding: 20px 30px 30px;
  background: #fff;
}

@media (min-width: 600px) {
  .panel {
    order: 99;
  }
}

.input:checked + .label + .panel {
  display: block;
}
</style>

```{r echo=FALSE, message=FALSE, purl=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
library(downloadthis)
library(here)
```

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read the Submission Directions
Please submit a PDF out using an Rmarkdown file for this task^[If you use an external file for your data, please submit that as well.]. Please submit a PDF using an Rmarkdown file for this task^[If you use an external file for your data, please submit that as well.] both to eCampus and [Slack](https://2021edp693e.slack.com/archives/C01PB0Z18FP){target="_blank"}.

You may use the data set provided in this week's walkthrough or any other valid set *with citations* to address the following criteria regarding **the 2016 general election**.<br><br>For each election year, do the following:

1. The differences between the popular and electoral college votes by *census tract*, *county*, and *state*. For each, show both the flat standard representation and where votes counts and/or percentages are displayed by size. For a example of a state level representation of this, please look [here](http://www-personal.umich.edu/~mejn/election/2016/){target="_blank"}.

2. How differing demographical subgroups voted. You should include at minimum *age*, *race* and *sex*^[Please use the applicable [U.S Census standard](https://www.census.gov/topics/population.html){target="_blank"} for these demographics.] and *at least three others of your choice*^[Need not be a criteria reported in the U.S. Census].

3. A *single* final visualization showing the differences in the popular and electoral college votes by *census tract*, *county*, and *state*.<br>
Please submit your output to both 

    - [eCampus](https://ecampus.wvu.edu){target="_blank"} and 

    - [Slack](https://2021edp693e.slack.com/archives/C01PTTDPTM5){target="_blank"} a `PDF` and/or `HTML` output using an Rmarkdown file for this task. 

4. Bonus! Display state^[of your choice] elections by *census tract* and *county*. 

:::