---
title: "Getting Started in Research"
linktitle: "Week 4: Getting Started in Research"
toc: true
output:
  rmarkdown::html_document:
    toc: true
menu:
  extras:
    parent: Extras
    weight: 4
type: docs
weight: 1
editor_options: 
  chunk_output_type: console
---

`r blogdown::shortcode("materials-header")`

```{r load_packages, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Myers-Briggs

This week we look at the [Myers–Briggs Type Indicator](https://www.myersbriggs.org/my-mbti-personality-type/mbti-basics/) (MBTI) personality inventory. Here are somethings to consider as you think about this assessment.

1. **There isn't a lot of definitive research**. By the title you may think that well designed quantitative studies do not exist - in fact they do. The problem in-lies in the idea that many of them aren't at all conclusive and at best provide us with some idea of what is going on. While you may have an opinion about the MBTI or personality assessments in general, when it comes to test validity and reliability we get a lot of polarized opinions, some small-scale research with very little consistency, and absolutely no true experimental studies that could give us usable results. 

2. **It's a race against time and space**. OK so so we're not talking about the concept of space-time that Einstein used to describe the universe, rather this is an issue related to growth and acceptance at the social level. While it might appear counterintuitive at first, any test that has both a (1) long history and an (2) increasing footprint diminishes our ability to assess its efficacy because we at some point can't tell the difference been causality and independence. Establishing Causal relationships - i.e. finding with certainty that one event<a href="#1"><sup>1</sup></a> directly affects another - is based on satisfying the three criteria listed below
<center>
```{r echo=FALSE}
tibble(
  
idea = c("<i>Change goes both ways</i>",
         "<i>It's cause and effect</i>",
         "<i>There's no other way</i>"),
  
  aka = c("Covariance",
          "Temporal precedence",
          "Nonspuriousness"),
  
  description = c("There is a known relationship between two events where if one changes so does the other",
                  "With respect to time, the cause of an comes before its effect",
                  "Every other likely explanation of the event has been ruled out"),
  
  .name_repair = "minimal"
  
) %>%
  kbl(col.names = c("Idea", "AKA",  "Description"),
      "html", 
      escape = FALSE,
      align = "lll") %>%
  kable_paper(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "20em") %>%
  row_spec(0:3, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent")
```
</center>

3. **Threats to Internal Validity**. We will explore this further but in a nutshell this is how confident someone is that a cause-and-effect relationship can't be explained by other factors. At some point the MBTI's footprint may become large enough that a significant portion of a population of people taking the assessment will have prior knowledge of test in a way they can knowingly or unknowingly affect the results.

To that end, we'll take a look at sources that absolutely use existing research to make a point about what the MBTI is and how it is used. While you can absolutely treat these as summaries of existing research, keep in mind they are written or told in a way to make a point which doesn't always mean that they are comprehensive.

### Videos

Here is a clip from the show *Adam Ruins Everything* that discusses the history of MBTI in a colorful way

<p align="center">
<iframe width="560" height="315" src="https://www.youtube.com/embed/_NQqSnkI32A" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</p>

A documentary titled *Persona: The Dark Truth Behind Personality Tests* is currently streaming on HBOmax. The trailer is provided below

<p align="center">
<iframe width="560" height="315" src="https://www.youtube.com/embed/XWBXniurrA0" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</p>

### Article

A look at the use of personality tests in general including MBTI within the workplace is provided in the 2019 New York Times article [*Personality Tests Are the Astrology of the Office*](https://www.nytimes.com/2019/09/17/style/personality-tests-office.html)<a href="#2"><sup>2</sup></a>

<br>
<hr align="center" width="50%">
<br>

<a id="1" href="#" onclick="history.back();" style="font-size:14px;"><sup>1</sup></a> <a style="font-size:14px;"> An <i>event</i> is just something that happens. In statistics its a bit more formalized and described as an <i>outcome or defined collection of outcomes of a random experiment</i>.</a>

<a id="2" href="#" onclick="history.back();" style="font-size:14px;"><sup>2</sup></a> <a style="font-size:14px;"> You will likely need access to a New York Times subscription to read this. As a WVU student, you can sign up for an academic pass which will provide you with free access for up to four years. More information can be found on the  <a href="https://databases.lib.wvu.edu/about/1434567915" target="_blank"><span style="font-size: 14px">WVU Libraries New York Times (Digital Edition) information page</span></a></a>
