---
title: "Who's Values Are Valuable?"
linktitle: "Week 5: Who's Values Are Valuable?"
output:
  rmarkdown::html_document
menu:
  extras:
    parent: Extras
    weight: 5
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

```{r load_packages, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
```

<style>
td, th, tr, table {
    border: 0 !important;
    border-spacing:0 !important;
  }
</style>

## Evaluation Phase
We are currently in the pre-evaluation phase. This involves

```{r echo = FALSE}

unchecked <- as.character(fontawesome::fa("circle", fill = "#e4e4e4", height = "15px"))

checked <- as.character(fontawesome::fa("check-circle", fill = "#428bca", height = "15px"))

pre <- tibble(
  
  phase = c("Pre-Evaluation",
            "",
            ""),
  
  task = c("Gathering a team",
           "Thinking about potential programs",
           "Submitting a prospectus"),
  
  current <- c(unchecked,
               unchecked,
               checked)
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
  pre %>%
  kbl(col.names = c("Phase", "Task", "Current"),
      "html",
      escape = FALSE,
      align = 'llc')  %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "20em") %>% 
  row_spec(0:3, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent")
```
</center>

## The Evaluators Toolbox

The [Center for Community Health and Development](https://ctb.ku.edu/en/evaluating-community-programs-and-initiatives) at the University of Kansas has a very comprehensive guide on developing an evaluation plan, identifying stakeholders interests, and conducting a participatory evaluation.

The link above is part of a much larger and highly detailed look at a type of evaluation framework known as [community engagement evaluation](https://ctb.ku.edu/en/table-of-contents) which is difficult, if not impossible to address fully in a semester.

