---
title: "The Importance of Knowing What's Important"
linktitle: "Week 6: The Importance of Knowing What's Important"
output:
  rmarkdown::html_document
menu:
  extras:
    parent: Extras
    weight: 6
type: docs
weight: 2
editor_options: 
  chunk_output_type: console
---

<style>
td, th, tr, table {
    border: 0 !important;
    border-spacing:0 !important;
  }
</style>

```{r load_packages, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
```

## Evaluation Phase

We are currently in the evaluation planning phase. This involves

```{r echo = FALSE}

unchecked <- as.character(fontawesome::fa("circle", fill = "#e4e4e4", height = "15px"))

checked <- as.character(fontawesome::fa("check-circle", fill = "#428bca", height = "15px"))

plan <- tibble(
  
  phase = c("Planning",
            ""),
  
  task = c("Discovering needs",
           "Suggesting a course of action"),
  
  current <- c(checked,
               unchecked)
  
)

```

<center>
```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
  plan %>%
  kbl(col.names = c("Phase", "Task", "Current"),
      "html",
      escape = FALSE,
      align = 'llc') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "20em") %>% 
  row_spec(0:2, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent")
```
</center>

## More Logic Models

As you begin to think about a logic model, you do not have to use the one provided. Please look around for others. For example, you may want to consider the comprehensive [logic models](https://fyi.extension.wisc.edu/programdevelopment/logic-models/) repository in the [Division of Extension @ The University of Wisconsin](https://fyi.extension.wisc.edu/programdevelopment/). 
