---
title: 'Analyzing Literature'
subtitle: "EDP 612 Week 6"
author: "Dr. Abhik Roy"
output: 
 xaringan::moon_reader:
   css: ['xaringan-themer.css', 'custom.css']
   nature:
     ratio: 16:9
     highlightStyle: github
     highlightLines: true
     countIncrementalSlides: false
     navigation:
         scroll: false
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.6.0/jquery.min.js"></script>

<script type="text/x-mathjax-config">
MathJax.Hub.Register.StartupHook("TeX Jax Ready",function () {
  MathJax.Hub.Insert(MathJax.InputJax.TeX.Definitions.macros,{
    cancel: ["Extension","cancel"],
    bcancel: ["Extension","cancel"],
    xcancel: ["Extension","cancel"],
    cancelto: ["Extension","cancel"]
  });
});
</script>

<style>
section {
    display: flex;
    display: -webkit-flex;
}

section p {
    margin: auto;
}

section {
    height: 600px;
    width: 60%;
    margin: auto;
    border-radius: 21px;
    background-color: #212121;
}

section p {
    text-align: center;
    font-size: 30px;
    background-color: #212121;
    border-radius: 21px;
    font-family: Roboto Condensed;
    font-style: bold;
    padding: 12px;
    color: #bff4ee;
}

#center {

text-align: center;

}

.center p {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.tab {
    display: inline-block;
    margin-left: 40px;
}
</style>

```{css echo=FALSE}
.highlight-last-item > ul > li,
.highlight-last-item > ol > li {
  opacity: 0.5;
}
.highlight-last-item > ul > li:last-of-type,
.highlight-last-item > ol > li:last-of-type {
  opacity: 1;
}
```

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(patchwork)
library(knitr)
library(kableExtra)
library(fontawesome)
library(here)
library(DT)
library(scales)
library(latex2exp)
library(rvest)
library(showtext)
font_add_google("Roboto Condensed", "roboto")
showtext_auto()
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#bff4ee",
  table_row_border_color = "#212121",
  table_row_even_background_color = "#212121",
  footnote_font_size = "0.6em",
  header_font_google = xaringanthemer::google_font("Roboto Condensed", "700"),
  text_font_google   = xaringanthemer::google_font("Roboto Condensed", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", 
                                    "animate_css", 
                                    "tachyons"))

xaringanExtra::use_logo(
  image_url = here::here("static", "img", "course_hex.png"),
  link_url = "https://edp612.asocialdatascientist.com",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
)

```

---

class: highlight-last-item
layout: true

---

#  Reference Text 

.center2[
<center>Please download</center><br><br>
[Machi, L.A., & McEvoy, B.T. (2021). The Literature Review: Six Steps to Success (4th ed.). SAGE Publications.](https://libwvu.on.worldcat.org/oclc/1289372718)
]

---

# Part I: Basic Overview

---

## Guideline 1 

--

+ Scan the articles to get an overview of each one

--

  + Read the first few paragraphs
	
--

	+ Read the entire Methods section

--

	+ Scan rest of article

---

## Guideline 2 


--

+ Based on your overview, group the articles by category

--

	+ By topics and then subtopics
	
--

	+ By chronological order within subtopic

---

## Guideline 3 

--

Note: This slide will sound like study skills but it is still highly recommended!

--

+ Organize yourself before reading the articles

--

	+ Computer
	
--

	+ Pack of note cards to write your comments on

--

	+ Self-adhesive flags that you can use to identify noteworthy comments (or word processing program to highlight)

---

## Guideline 4

--

+ Use a consistent format in your notes

--

	+ Example
	
--

		+ Author(s)’ Last Name(s), Initial(s)
		
--

		+ Title of Article

--
	
		+ Publication Year
		
--

		+ Name of Journal, Volume, Edition, Page Numbers
		
--

		+ Notes

---

## Guideline 5 
		
--

+ Look for explicit definitions of key terms in the literature

---

## Guideline 6
		
--

+ Look for methodological strengths

---

## Guideline 7
		
--

+ Look for methodological weaknesses

---

## Guideline 8
		
--

+ Distinguish between assertion and evidence
		
--

	+ Assertion = author’s opinion
		
--

	+ Evidence = results of study

---

## Guideline 9
		
--

+ Identify the major trends or patterns in the results of previous studies

--

+ Generalization based on sources included in literature review

---

## Guideline 10
		
--

+ Identify gaps in the literature

---

## Guideline 11 
		
--

+ Identify relationships among studies

---

## Guideline 12
		
--

+ Note how each reviewed article relates to your topic

---

## Guideline 13
		
--
 
+ Evaluate your reference list for relevancy and coverage
		
--

	+ Should demonstrate latest work done in subject area

---

# Part II: Analyzing Literature from the Viewpoint of a Researcher

---

## Guideline 1 

+ State whether the study is quantitative or qualitative		

--

	+ Research is neither quantitative or qualitative
			
--

  + So please do not say *the research was...*

---

## Guideline 2 	

--

+ Determine whether a study is experimental or nonexperimental	

--

	+ *Experimental*. Treatments are administered to participants for the purposes of the study and their effects are assessed	

--

	+ *Nonexperimental*. Participants’ traits are measured without attempting to change them

---

## Guideline 3 	

--

+ In an experiment, note whether the participants were assigned at random to treatment conditions	

--

	+ *True experiment*. Participants randomly assigned to treatment and control groups

---

## Guideline 4	

--

+ Note attempts to examine cause-and-effect issues in nonexperimental studies	

--

	+ *Causal-comparative*. Uncover relationships between independent and dependent variables after an action or event has already occurred
	
--
	
  > aka *retroactive* 
  
--
	
  > aka *ex post facto*

---

## Guideline 5 

+ Note how the major variables were measured

--

	+ *Valid*. Measure what they claim to measure
	
--

	+ *Reliable*. Yield consistent results

---

## Guideline 6

--
 
+ Note the characteristics of the samples of participants, such as

--

	+ Demographics

--

	+ Geographic location
	
--

	+ Gender
	
--

	+ Race
	
--

	+ Ethnicity
	
--

	+ Age
	
--

	+ SES

---

## Guideline 7
	
--

+ Note how large a difference is – not just whether it is statistically significant
	
--

+ So don't just report the $p$-value which by itself is nonsense

---

## Guideline 8 
	
--

+ It is safe to presume that all empirical studies are flawed
	
--

+ Never ever ever ever use the word "prove" when discussing results

---

# Guideline 9

--

> Make note of the limitations within each study

<br>
<br>

--

.pull-left[
These <span style="color:#d9534f;font-weight:bold;">are not</span> limits placed on<br>your own study due to another study!
]
  
--

.pull-right[
These <span style="color:#428bca;font-weight:bold;">are</span> constraints placed on the<br>ability to generalize from the results
]

--

<br>
<br>
<br>
> Given enough of a pattern, this provides you with justification to conduct a study of your own without infringing on another 

--

>> Found by summarizing and synthesizing

--

>> Ultimate purpose of the literaure review!


---

#  That’s it! 

Any questions?