---
title: "Testing Hypothesis and Measuring Confidence"
linktitle: "Week 9: Confidence Intervals"
author: "Week 9"
output: 
 xaringan::moon_reader:
   css: xaringan-themer.css
---

```{r setup, include=FALSE, purl=FALSE}
library(tidyverse)
library(fontawesome)
library(knitr)
library(kableExtra)
```

```{r echo = FALSE, purl=FALSE}
xaringanthemer::style_duo(
  primary_color = "#212121",
  secondary_color = "#fcbb86",
  text_bold_color = "#fc868c",
   code_inline_color = "#86c7fc",
  header_font_google = xaringanthemer::google_font("Jost", "600"),
  text_font_google   = xaringanthemer::google_font("Jost", "400")
)

xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
```

# Packages needed and a Note about Icons

Please load up the following packages. Remember to first install the ones you don't have.
```{r echo = FALSE, eval = TRUE, message=FALSE}
library(tidyverse)
library(mosaic)
library(ggplot2movies)
``` 

```{r echo = FALSE, eval = TRUE, message=FALSE}
suppressMessages(library(tidyverse))
suppressMessages(library(mosaic))
suppressMessages(library(ggplot2movies))
``` 
<br>
<br>
You may come across the following icons. The table below lists what each means.
```{r eval = TRUE, echo = FALSE, purl=FALSE}
forward <- as.character(fontawesome::fa("forward", fill = "
#4682b4"))

stop <- as.character(fontawesome::fa("stop", fill = "#ff6347"))

link <- as.character(fontawesome::fa("link", fill = "#5cb85c"))

bookmark <- as.character(fontawesome::fa("bookmark", fill = "#5cb85c"))


icon_desc <- tibble(
  
  Icon = c(forward,
           stop, 
           link,
           bookmark),
  
  Description = c("Indicates that an example continues on the following slide.",
                  "Indicates that a section using common syntax has ended.",
                  "Indicates that there is an active hyperlink on the slide.",
                  "Indicates that a section covering a concept has ended.")
  
)
```

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, purl=FALSE}
kable(icon_desc, 
      escape = FALSE,
      align = 'cl') %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "40em") %>%
  row_spec(0, background = "#181818") %>%
  row_spec(1, background = "#181818") %>%
  row_spec(2, background = "#181818") %>%
  row_spec(3, background = "#181818") %>%
  row_spec(4, background = "#181818") 
```

---

# What is a confidence interval?

A *confidence interval* (CI) gives a range of possible values for a parameter.  It depends on a specified _confidence level_ with 
- higher confidence levels corresponding to wider confidence intervals and 
- lower confidence levels corresponding to narrower confidence intervals.  

The most common confidence levels include 90%, 95%, and 99%.

---

# Problems with how confidence intervals are taught

Not to trash your professor, but you were taught about the confidence interval in a bad way! Traditionally, the way to find confidence intervals for some mean is to first assume a normal curve for a population and then magic. Sure its easy enough to follow procedurally, but the process is nether intuitive nor is it fantastic for people whose strong suit isn't mathematics.

---

# Enter a fancy term called bootstrapping (that you've already done)

In most studies, we simply want to if our null or alternative hypothesis is correct. More than that, the overall purpose of a hypothesis test is to answer this for an entire population,using the data we have - ergo to generalize.

We typically only have a sample of the population’s data to work with^[If we had the population, there's not much of a purpose to generalize]. So working with what we have in the most efficient and useful way is essential. Recently you 

1. took repeated samples from a sample data of size whatever,
2. calculate the mean for each of these samples,  
3. created a new distribution of these means, and
4. hopefully recognized with enough of these sample means, you can actually estimate the population distribution.

That is what is known as **bootstrapping**

---

## Thats it!